---
title: "Country Cases"
params: 
  optimize: true
---

```{r setup, include = FALSE}
source("_R/setup.R")
```

## Dataset 

All the figures below are based on a large global dataset (and accompanying codebook) which I assembled from commonly used quantitative indicators on health, gender equality and several types of violence. (The codebook, including variable definitions and summary statistics, is available as a Googlesheet in the shared Google Drive of the Metrics Working Group, or at this [link](https://docs.google.com/spreadsheets/d/1KLFTva--XHVBM-IX6qaPtuyzmIlRMnpyjUXfBdJPsag/edit?usp=sharing); access via logging into the shared folder provides more functionality. The dataset is available in the shared Dropbox folder of the Working Group.) 

```{r startup}
IsTrue <- function(x) { !is.na(x) & x }
load("_data/LSCMWG_working_data.RData", verbose = TRUE)
load("_data/dataset_LSCMWG.RData", verbose = TRUE)
```

```{r figure_function}
MakeFigure <- function(variable, countries = c("Afghanistan", "Mozambique", "El Salvador")) {
  dat <- data[data$country %in% countries, c("year", "country", variable)]
  first_year <- min(dat$year[!is.na(dat[, variable])])
  ggplot(dat, aes(x = year, y = !!sym(variable), group = country, color = country)) + 
    stat_summary(fun = "mean", geom = "line", na.rm = TRUE, size = 1) + 
    stat_summary(fun = "mean", geom = "point", na.rm = TRUE, size = 3) + 
    xlim(first_year, 2019) + theme_bw() + ggtitle(paste(variable))
}
```

## Health
```{r health, results = 'hide'}
lapply(variables$health_full, MakeFigure)
```

## Gender
```{r gender, results = 'hide'}
lapply(variables$gender_full, MakeFigure)
```

## Violence
```{r violence, results = 'hide'}
lapply(c("Afghanistan", "Mozambique", "El Salvador"), function(country) {
  dat <- data[data$country == country, ]
  dat <- dat %>% select(year, deaths_all_ext_rate, deaths_civilians_ext_rate, deaths_all_int_rate,
                        deaths_civilians_int_rate, deaths_all_osv_rate, deaths_civilians_osv_rate,
                        deaths_all_nsc_rate, deaths_civilians_nsc_rate, deaths_all_ucdp_rate, 
                        hom_odcwho_rate) %>% 
    gather(key = "variable", value = "value", -year)
  dat <- na.omit(dat)
  ggplot(dat, aes(x = year, y = value)) + 
    geom_point(aes(color = variable), size = 3) + 
    geom_line(aes(color = variable), size = 1) + 
    theme_bw() + ggtitle(country)
})
```
