---
title: "Classifications"
params: 
  cache: false
  optimize: true
---

```{r setup, include = FALSE}
source("setup.R")
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r startup}
IsTrue <- function(x) { !is.na(x) & x }
load("_data/LSCMWG_working_data.RData")
```

### {.tabset .tabset-fade .tabset-pills}

#### Classification with two variables on each dimensions for 1990

```{r classification}
Classification <- function(health, gender, 
  df = data, 
  year_to_show = 1995, 
  min_to_include = 2 # this is not implemented well but works for the current setup
){
  qs <- paste("q", 1:5, sep = "") 
  vars = c(health, gender)
  df <- df[, c("country", "year", "period", vars)]
  ## creating 5-year averages
  df <- df %>% group_by(country, period) %>% 
    mutate(across(all_of(vars), ~mean(.x, na.rm = TRUE), .names = "{col}_avg"), .keep = "all")
  df <- df %>%
    filter(year %in% seq(1970, 2015, 5)) %>%    # I removed 2018 here, for consistent panels, with downstream implications
    group_by(year)
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[2], .names = "{col}_q20"))
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[3], .names = "{col}_q40"))
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[4], .names = "{col}_q60"))
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[5], .names = "{col}_q80"))
  df <- ungroup(df)
  df[, paste(vars, "quintile", sep = "_")] <- parallel::mclapply(vars, function(var) {
    col <- rep(NA, nrow(df))
    col[df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q20", sep = "_")]] <- 1
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q20", sep = "_")] & 
      df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q40", sep = "_")]] <- 2
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q40", sep = "_")] &
      df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q60", sep = "_")]] <- 3
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q60", sep = "_")] &
      df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q80", sep = "_")]] <- 4
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q80", sep = "_")]] <- 5
    return(col)
  })
# df <- df[, c("country", "year", "period", names(df)[str_detect(names(df), fixed("quintile"))])]
  # combis <- expand.grid(health = health, gender = gender, stringsAsFactors = FALSE)
  # combis <- split(combis, seq(nrow(combis)))
  df$health_q1 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 1, na.rm = TRUE)
  df$health_q2 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 2, na.rm = TRUE)
  df$health_q3 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 3, na.rm = TRUE)
  df$health_q4 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 4, na.rm = TRUE) 
  df$health_q5 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 5, na.rm = TRUE) 
  df$gender_q1 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 1, na.rm = TRUE) 
  df$gender_q2 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 2, na.rm = TRUE) 
  df$gender_q3 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 3, na.rm = TRUE) 
  df$gender_q4 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 4, na.rm = TRUE) 
  df$gender_q5 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 5, na.rm = TRUE)
  health_vars <- paste("health", qs, sep = "_")
  gender_vars <- paste("gender", qs, sep = "_")
  df$health_valid <- rowSums(df[, health_vars])
  df$gender_valid <- rowSums(df[, gender_vars])
  df$valid <- df$health_valid * df$gender_valid
  # unique(df$country[df$valid  == 0])
  df <- df[df$valid > 0, ]
  ### version based on the standardized vars
  new <- df[, c("country", "year", paste(vars, "avg", sep = "_"))] %>%
    group_by(year) %>%
    mutate(across(paste(vars, "avg", sep = "_"), ~as.numeric(scale(.x)), .names = "{col}")) %>%
    mutate(health = (imr_wpp_avg + life_exp_wpp_avg)/2, 
           gender = (asfr_adol_wpp_avg + mys_age_ratio_ihme_avg)/2) %>% 
    select(country, year, health, gender) %>% 
    ungroup()
  new$health_class[new$health >= quantile(new$health, probs = seq(0, 1, 0.2), na.rm = TRUE)[1]] <- 1
  new$health_class[new$health >= quantile(new$health, probs = seq(0, 1, 0.2), na.rm = TRUE)[2]] <- 2
  new$health_class[new$health >= quantile(new$health, probs = seq(0, 1, 0.2), na.rm = TRUE)[3]] <- 3
  new$health_class[new$health >= quantile(new$health, probs = seq(0, 1, 0.2), na.rm = TRUE)[4]] <- 4
  new$health_class[new$health >= quantile(new$health, probs = seq(0, 1, 0.2), na.rm = TRUE)[5]] <- 5
  new$gender_class[new$gender >= quantile(new$gender, probs = seq(0, 1, 0.2), na.rm = TRUE)[1]] <- 1
  new$gender_class[new$gender >= quantile(new$gender, probs = seq(0, 1, 0.2), na.rm = TRUE)[2]] <- 2
  new$gender_class[new$gender >= quantile(new$gender, probs = seq(0, 1, 0.2), na.rm = TRUE)[3]] <- 3
  new$gender_class[new$gender >= quantile(new$gender, probs = seq(0, 1, 0.2), na.rm = TRUE)[4]] <- 4
  new$gender_class[new$gender >= quantile(new$gender, probs = seq(0, 1, 0.2), na.rm = TRUE)[5]] <- 5
  new$class <- paste("H", new$health_class, "G", new$gender_class, sep = "")
  tab_st <- new %>% filter(year == year_to_show)
  n_st <- table(health = tab_st$health_class, gender = tab_st$gender_class)
  dimnames(n_st) <- lapply(dimnames(n_st), function(name) { paste("Q", name, sep = "") })
  tab_st <- tapply(tab_st$country, list(health = tab_st$health_class, gender = tab_st$gender_class), paste, collapse = "; ")
  tab_st[is.na(tab_st)] <- ""
  dimnames(tab_st) <- lapply(dimnames(tab_st), function(name) { paste("Q", name, sep = "") })
  ### back to original version
  df <- df[, !names(df) %in% unlist(lapply(c("q20", "q40", "q60", "q80", "quintile", health, gender), function(x) names(df)[str_detect(names(df), x)]))]
  health_true <- df[, health_vars] == apply(df[, health_vars], MARGIN = 1, FUN = max)
  gender_true <- df[, gender_vars] == apply(df[, gender_vars], MARGIN = 1, FUN = max)
  health_help <- health_true * matrix(1:5, nrow = nrow(health_true), ncol = 5, byrow = TRUE)
  gender_help <- gender_true * matrix(1:5, nrow = nrow(gender_true), ncol = 5, byrow = TRUE)
  help_floor <- function(set) { return(floor(mean(set[set != 0]))) }
  help_ceiling <- function(set) { return(ceiling(mean(set[set != 0]))) }
  df$health_class <- apply(health_help, MARGIN = 1, help_floor)
  df$gender_class <- apply(gender_help, MARGIN = 1, help_floor)
  df$health_class_alt <- apply(health_help, MARGIN = 1, help_ceiling)
  df$gender_class_alt <- apply(gender_help, MARGIN = 1, help_ceiling)
  df$health_flag <- ifelse(df$health_class != df$health_class_alt, 1, 0)
  df$gender_flag <- ifelse(df$gender_class != df$gender_class_alt, 1, 0)
  health_index <- paste("health_q", df$health_class, sep = "")
  gender_index <- paste("gender_q", df$gender_class, sep = "")
  df$health_n <- unlist(lapply(1:length(health_index), function(index) { 
    as.integer(df[index, health_index[index]]) 
  }))
  df$gender_n <- unlist(lapply(1:length(gender_index), function(index) { 
    as.integer(df[index, gender_index[index]]) 
  }))
  df$combi <- df$health_n * df$gender_n
  df$class <- paste("H", df$health_class, "G", df$gender_class, sep = "")
  df$class_alt <- paste("H", df$health_class_alt, "G", df$gender_class_alt, sep = "")
  test <- table(df[df$year == year_to_show & df$valid >= min_to_include, c("health_class", "gender_class")])
  # print(test)
  number_of_countries <- sum(test)
  df$support <- paste(df$country, " (", df$combi, "/", df$valid, ")", sep = "")
  dat <- df[df$year == year_to_show, ]
  table_to_return <- tapply(dat$support, 
                            INDEX = list(health = dat$health_class, gender = dat$gender_class), 
                            paste, collapse = "; ")
  table_to_return[is.na(table_to_return)] <- ""
  dimnames(table_to_return) <- lapply(dimnames(table_to_return), function(name) { paste("Q", name, sep = "") })
  ## from here, this is the old way, to create the fuzzy table, not needed anymore but useful for comparison
  df$H1G1 <- df$health_q1 * df$gender_q1
  df$H2G1 <- df$health_q2 * df$gender_q1
  df$H3G1 <- df$health_q3 * df$gender_q1
  df$H4G1 <- df$health_q4 * df$gender_q1
  df$H5G1 <- df$health_q5 * df$gender_q1
  df$H1G2 <- df$health_q1 * df$gender_q2
  df$H2G2 <- df$health_q2 * df$gender_q2
  df$H3G2 <- df$health_q3 * df$gender_q2
  df$H4G2 <- df$health_q4 * df$gender_q2
  df$H5G2 <- df$health_q5 * df$gender_q2
  df$H1G3 <- df$health_q1 * df$gender_q3
  df$H2G3 <- df$health_q2 * df$gender_q3
  df$H3G3 <- df$health_q3 * df$gender_q3
  df$H4G3 <- df$health_q4 * df$gender_q3
  df$H5G3 <- df$health_q5 * df$gender_q3
  df$H1G4 <- df$health_q1 * df$gender_q4
  df$H2G4 <- df$health_q2 * df$gender_q4
  df$H3G4 <- df$health_q3 * df$gender_q4
  df$H4G4 <- df$health_q4 * df$gender_q4
  df$H5G4 <- df$health_q5 * df$gender_q4
  df$H1G5 <- df$health_q1 * df$gender_q5
  df$H2G5 <- df$health_q2 * df$gender_q5
  df$H3G5 <- df$health_q3 * df$gender_q5
  df$H4G5 <- df$health_q4 * df$gender_q5
  df$H5G5 <- df$health_q5 * df$gender_q5
  vars <- c("H1G1", "H2G1", "H3G1", "H4G1", "H5G1", 
            "H1G2", "H2G2", "H3G2", "H4G2", "H5G2", 
            "H1G3", "H2G3", "H3G3", "H4G3", "H5G3", 
            "H1G4", "H2G4", "H3G4", "H4G4", "H5G4", 
            "H1G5", "H2G5", "H3G5", "H4G5", "H5G5")
  names(vars) <- vars
  dat <- as.data.frame(df[df$year == year_to_show, c("country", "valid", vars)])
  classifications <- parallel::mclapply(vars, function(var_name) {
    new <- dat[dat[, var_name] >= min_to_include, c("country", var_name, "valid")]
    countries <- new$country
    new <- paste(new[, "country"], " (", new[, var_name], "/", new[, "valid"], ")", sep = "")
    new <- new[new != " (/)"]    
    return(list(class = new, ctry = countries))
  })
  countries <- sort(unique(unlist(lapply(classifications, function(x) { x$ctry }))))
  classifications <- lapply(classifications, function(class) { class$class })
  classifications <- lapply(classifications, paste, collapse = "; ")
  # print(matrix(names(classifications), 5, 5, dimnames = list(health = qs, gender = qs)))
  fuzzy_table <- matrix(classifications, 5, 5, dimnames = list(health = qs, gender = qs))
  # if(number_of_countries != length(countries)) {
  #   cat("\nNot classifying the same number of countries as the fuzzy way!")
  # }
  df <- df[, !names(df) %in% vars]
  return(list(df = df, n = test, table = table_to_return, fuzzy = fuzzy_table, standardized = new, table_st = tab_st, n_st = n_st))  
}
result <- Classification(health = variables$health, gender = variables$gender, year_to_show = 1995)
kableExtra::kable(result$table, format = "html") %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::add_header_above(c(" " = 1, "Gender" = 5)) %>% 
  kableExtra::group_rows("Health", 1, 5)
# sum(result$n_st)
# xtable::xtable(result$n_st)
```

#### Fuzzy version of classification 
```{r fuzzy}
kableExtra::kable(result$fuzzy, format = "html") %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::add_header_above(c(" " = 1, "Gender" = 5)) %>% 
  kableExtra::group_rows("Health", 1, 5)
```

#### New version of classification based on standardized data
```{r classification_new}
kableExtra::kable(result$table_st, format = "html") %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::add_header_above(c(" " = 1, "Gender" = 5)) %>% 
  kableExtra::group_rows("Health", 1, 5)
```

<!-- ### Classification using the performance versions of the health and gender inputs -->
```{r perf, eval = FALSE, echo = FALSE}
result_perf <- Classification(health = paste("perf", variables$health, sep = "_"), 
                              gender = paste("perf", variables$gender, sep = "_"), year_to_show = 1995)
kableExtra::kable(result_perf$table, format = "html") %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::add_header_above(c(" " = 1, "Gender" = 5)) %>% 
  kableExtra::group_rows("Health", 1, 5)
```

<!-- #### Merging classifications into dataset -->
```{r merging}
variables$class <- c("class", "health_class", "gender_class", "health_class_alt", "gender_class_alt", "health_flag", "gender_flag")
df <- as.data.frame(result$standardized[, names(result$standardized) %in% c("country", "year", variables$class)])
# flagged <- df[df$year == 1990 & (df$health_flag == 1 | df$gender_flag == 1), c("country", variables$class)]
df$class_vv <- NA
df$class_vv[df$health_class < 3 & df$gender_class < 3] <- "low"
df$class_vv[df$health_class > 3 & df$gender_class > 3] <- "upp"
df$class_vv[!(df$health_class < 3 & df$gender_class < 3) & !(df$health_class > 3 & df$gender_class > 3)] <- "mid"
df$class_vv[df$class_vv == "mid" & df$health_class > df$gender_class] <- "H>G"
df$class_vv[df$class_vv == "mid" & df$health_class < df$gender_class] <- "G>H"
## alt
# df$class_vv_alt <- NA
# df$class_vv_alt[df$health_class_alt < 3 & df$gender_class_alt < 3] <- "low"
# df$class_vv_alt[df$health_class_alt > 3 & df$gender_class_alt > 3] <- "upp"
# df$class_vv_alt[!(df$health_class_alt < 3 & df$gender_class_alt < 3) & !(df$health_class_alt > 3 & df$gender_class_alt > 3)] <- "mid"
# df$class_vv_alt[df$class_vv_alt == "mid" & df$health_class_alt > df$gender_class_alt] <- "H>G"
# df$class_vv_alt[df$class_vv_alt == "mid" & df$health_class_alt < df$gender_class_alt] <- "G>H"
# addmargins(table(df$class_vv, df$class))
df$class_low <- ifelse(df$class_vv == "low", 1, 0)
df$class_upp <- ifelse(df$class_vv == "upp", 1, 0)
df$class_mid <- ifelse(df$class_vv == "mid", 1, 0)
df$class_HG <- ifelse(df$class_vv == "H>G", 1, 0)
df$class_GH <- ifelse(df$class_vv == "G>H", 1, 0)
variables$class_core <- c("country", "class", "health_class", "gender_class", "class_vv")
class1975 <- df[df$year == 1975, variables$class_core]
names(class1975) <- c("country", paste(c("class", "health", "gender", "class_vv"), 1975, sep = ""))
class1990 <- df[df$year == 1990, variables$class_core]
names(class1990) <- c("country", paste(c("class", "health", "gender", "class_vv"), 1990, sep = ""))
class1995 <- df[df$year == 1995, variables$class_core]
names(class1995) <- c("country", paste(c("class", "health", "gender", "class_vv"), 1995, sep = ""))
df <- merge(data, df, by = c("country", "year"), all = TRUE)
df <- merge(df, class1975, by = "country", all.x = TRUE)
df <- merge(df, class1990, by = "country", all.x = TRUE)
df <- merge(df, class1995, by = "country", all.x = TRUE)
df <- df[order(df$country, df$year), 
         c("country", "year", "period", names(df)[!names(df) %in% c("country", "year", "period")])]
filepath <- paste("~/Dropbox/Lancet-SIGHT Commission/Working Groups/Metrics/Datasets/dataset_cy_class", ".csv", sep = "" )
write_csv(df, file = filepath)
```

<!-- #### Subset of 1990 classifications for which "floor" rule was applied -->
```{r flagged, eval = FALSE, echo =FALSE}
flagged
```

<!-- ### Classification trajectories (in 5-year increments based on global distributions in same time period) -->
```{r class_time, echo = FALSE, eval = FALSE, fig.width = 14, fig.height = 10, out.width = "100%", out.height = "100%"}
df$class_num <- df$health_class * df$gender_class
ggplot(data = df[df$year %in% c(seq(1965, 2015, 5), 2018), ]) + 
  geom_line(aes(x = year, y = class_num)) + 
  facet_wrap(~country) +
  theme_classic() + 
  scale_x_continuous(breaks = seq(1970, 2010, by = 20))
```

<!-- ### Descriptives of control variables by 1990 classification: mean (SD) -->
```{r descriptives, echo = FALSE, eval = FALSE}
Descriptives <- function(cell, digits = 2) {
  mean <- mean(cell, na.rm = TRUE)
  sd <- sd(cell, na.rm = TRUE)
  ifelse(!is.na(mean), paste(round(mean, digits), " (", round(sd, digits), ")", sep = ""), "")
}
table_to_show <- lapply(variables$controls, function(var) {
  to_return <- tapply(df[, var], 
                      INDEX = list(health = df$health1990, gender = df$gender1990), 
                      FUN =  Descriptives)
  to_return[is.na(to_return)] <- ""
  return(to_return)
})
noquote(table_to_show)
```

#### Which countries move more than 2 cells?
```{r movers}
df$class_num <- df$health_class * df$gender_class
names(years) <- years <- c(1990, 1995, 2015)
dat <- lapply(years, function(year) {
  df <- as.data.frame(df[df$year == year, c("country", "class_num")])
  names(df)[2] <- paste("class", year, sep = "")
  return(df)
})
dat <- Reduce(f = function(...) merge(..., by = "country", all = TRUE), x = dat)
dat$diff <- dat$class2015 - dat$class1990
dat$diff_alt <- dat$class2015 - dat$class1995
better <- dat[IsTrue(dat$diff > 2 | dat$diff_alt > 2), ]
worse <- dat[IsTrue(dat$diff < -2 | dat$diff_alt < -2), ]
better 
worse
```

#### Removing countries with untrustworthy statistics 

All data is subject to measurement error. This is particularly problematic if measurement is systematically biased. Without other data to validate a given measure, this is a very difficult to problem to overcome. We only use data from reputable sources, such as academic centre and international organizations, but some self-reported data are still suspect. The World Bank and some NGOs have attempted to rate the capacity of National Statistical System, and some countries are not inlcuded in their rankings because assessments could be not be made based on available information. For instance, the ODIN rankings from 2015 to 2018 do not include the Central African Republic, Eritrea, Equatorial Guinea, and North Korea. Interestingly, among these, only North Korea is relatively highly ranked on the gender and health dimensions according to these data, which is simply not believable. Therefore, we remove only North Korea from the analyses.

```{r capacity}
df <- df[df$country != "North Korea", ]
```

#### Trends by classification groups over time {.tabset .tabset-fade .tabset-pills}

##### Life expectancy
```{r trend_life, fig.width = 12, fig.height = 8}
df$class_vv <- factor(df$class_vv, levels = c("low", "G>H", "H>G", "mid", "upp"))
df %>%
  filter(year >= 1970 & !is.na(class_vv)) %>%
  group_by(year) %>%
  ggplot() + 
    stat_summary(mapping = aes(x = year, y = life_exp_wpp, group = class_vv, color = class_vv), 
                 fun = mean, geom = "line") + 
    stat_summary(mapping = aes(x = year, y = life_exp_wpp), 
                 fun = mean, geom = "line", color = "gray") + 
    labs(x = "", y = "", color = "Classifications") + 
    theme_minimal() + 
    theme(legend.position = "top")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/trend_life_exp_wpp.pdf")
```

##### IMR
```{r trend_imr, fig.width = 12, fig.height = 8}
df %>%
  filter(year >= 1970 & !is.na(class_vv)) %>%
  group_by(year) %>%
  ggplot() + 
    stat_summary(mapping = aes(x = year, y = -imr_wpp, group = class_vv, color = class_vv), 
                 fun = mean, geom = "line") + 
    stat_summary(mapping = aes(x = year, y = -imr_wpp), 
                 fun = mean, geom = "line", color = "gray") + 
    labs(x = "", y = "", color = "Classifications") + 
    theme_minimal() + 
    theme(legend.position = "top")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/trend_imr_wpp.pdf")
```

##### MYS
```{r trend_mys, fig.width = 12, fig.height = 8}
df %>%
  filter(year >= 1970 & !is.na(class_vv)) %>%
  group_by(year) %>%
  ggplot() + 
    stat_summary(mapping = aes(x = year, y = mys_age_ratio_ihme, group = class_vv, color = class_vv), 
                 fun = mean, geom = "line") + 
    stat_summary(mapping = aes(x = year, y = mys_age_ratio_ihme), 
                 fun = mean, geom = "line", color = "gray") + 
    labs(x = "", y = "", color = "Classifications") + 
    theme_minimal() + 
    theme(legend.position = "top")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/trend_mys_age_ratio_ihme.pdf")
```

##### ASFR
```{r trend_asfr, fig.width = 12, fig.height = 8}
df %>%
  filter(year >= 1970 & !is.na(class_vv)) %>%
  group_by(year) %>%
  ggplot() + 
    stat_summary(mapping = aes(x = year, y = -asfr_adol_wpp, group = class_vv, color = class_vv), 
                 fun = mean, geom = "line") + 
    stat_summary(mapping = aes(x = year, y = -asfr_adol_wpp), 
                 fun = mean, geom = "line", color = "gray") + 
    labs(x = "", y = "", color = "Classifications") + 
    theme_minimal() + 
    theme(legend.position = "top")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/trend_asfr_adol_wpp.pdf")
```

#### Trends by 1995 classification groups {.tabset .tabset-fade .tabset-pills}

##### Health & gender
```{r categories, results = 'hide'}
summary(as.factor(df$class_vv1990))
summary(as.factor(df$class_vv1995))
lapply(c(variables$health_full, variables$gender_full), function(var) {
  dat <- df[!is.na(df$class_vv1995) & df$class_vv1995 != "mid", ]
  ggplot(dat, aes(x = year, y = !!sym(var), group = class_vv1995, color = class_vv1995)) + 
    stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
    xlim(1980, 2018) + 
    theme_bw() + 
    ggtitle(paste(var, "average by 1995 classification over time"))
})
```

##### Cumulative death rates
```{r deaths, results = 'hide'}
lapply(variables$death_rates, function(var) {
  dat <- df[!is.na(df$class_vv1995) & df$class_vv1995 != "mid", ]
  ggplot(dat, aes(x = year, y = log(!!sym(paste(var, "cumulative1991", sep = "_")) + 1), 
                  group = class_vv1995, color = class_vv1995)) + 
    stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
    xlim(1990, 2018) + 
    theme_bw() + 
    ggtitle(paste(var, "annual cumulative average (logged) since 1991 by 1995 classification"))
})
```

##### Cumulative repression
```{r violence, results = 'hide'}
lapply(variables$measurement_models, function(var) {
  dat <- df[!is.na(df$class_vv1995) & df$class_vv1995 != "mid", ]
  ggplot(dat, aes(x = year, y = !!sym(paste(var, "cumulative1991", sep = "_")), 
                  group = class_vv1995, color = class_vv1995)) + 
  stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
  xlim(1990, 2018) + 
  theme_bw() + 
  ggtitle(paste(var, "annual cumulative average since 1991 by 1995 classification"))
})
```

##### Conflict incidence
```{r incidence, results = 'hide'}
lapply(variables$conflict_incidence, function(var) {
  dat <- df[df$year > 1988, ]
  tbl <- tapply(dat[, var], list(health = dat$health1995, gender = dat$gender1995), mean, na.rm = TRUE)
  dat <- dat[!is.na(dat$class_vv1995) & dat$class_vv1995 != "mid", ]
  plot <- ggplot(dat, aes(x = year, y = !!sym(var), group = class_vv1995, color = class_vv1995)) + 
    stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
    xlim(1989, 2018) + 
    theme_bw() + 
    ggtitle(paste(var, " incidence by classification in 1995"))
  return(list(tbl, plot))
})
```

<!-- #### Mean growth rates by classification with t-test (alt H: mean different from global) -->
```{r growth_rates, echo = FALSE, eval = FALSE}
GrowthRatesTtest <- function(var, min_obs = 2) { 
  dat1995 <- df[df$year == 1995, c("country", "class", "health_class", "gender_class", var)]
  dat2015 <- df[df$year == 2015, c("country", var)]
  names(dat1995)[names(dat1995) != "country"] <- paste(names(dat1995)[names(dat1995) != "country"] , 
                                                       1995, sep = "_")
  names(dat2015)[names(dat2015) != "country"] <- paste(names(dat2015)[names(dat2015) != "country"] , 
                                                       2015, sep = "_")
  dat <- merge(dat1995, dat2015, by = c("country"), all = TRUE)
  dat$growth <- dat[, paste(var, 2015, sep ="_")] - dat[, paste(var, 1995, sep ="_")]
  tbl <- tapply(dat$growth, list(health = dat$health_class_1995, gender = dat$gender_class_1995), function(df) {
    if(sum(!is.na(df)) >= min_obs) {
      result <- t.test(df, mu = mean(dat$growth, na.rm = TRUE))
      mean <- round(result[["estimate"]][["mean of x"]], 2)
      pvalue <- round(result[["p.value"]], 2)
      df <- result[["parameter"]][["df"]]
      cell <- paste(mean, " (p-value ", pvalue, "; df ", df, ")", sep = "")
    } else { cell <- "" }
    return(cell)
  })
  tbl[is.na(tbl)] <- ""
  return(list(global_mean = mean(dat$growth, na.rm = TRUE), ttests = noquote(tbl)))
}
variables$outcomes <- c(variables$health_full, variables$gender_full, variables$death_rates, variables$measurement_models)
parallel::mclapply(variables$outcomes, GrowthRatesTtest)
```

<!-- #### Preparing cross-sectional dataset -->
```{r reg_prep}
covariates <- c("pc_rgdpe_pwt", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "mys_age_ratio_ihme", "asfr_adol_wpp")
covariates <- paste(covariates, "avg", sep = "_")
# covariates <- c(covariates, "oda_provided_const_wdi", "oda_received_perc_gov_exp_wdi", "oda_aid_received_const_wdi", "oda_received_const_wdi", "oda_received_perc_imports_wdi", "aid_received_const_wdi")
vars <- unlist(lapply(covariates, function(var) { names(df)[str_detect(names(df), var)] }))
vars <- unique(vars[vars != "pasfr_adol_wpp"])
include <- c("country", "class", "class_vv", "class_low", "class_upp", vars)
new1990 <- df[df$year == 1990, c(include, variables$death_rates, variables$measurement_models)]
new1995 <- df[df$year == 1995, c(include, variables$death_rates, variables$measurement_models, 
  paste(variables$conflict_incidence, "cumulative1989", sep = "_"),
  paste(variables$political, "cumulative1991", sep = "_"))]
new2015 <- df[df$year == 2015, c(include, 
  paste(c(variables$death_rates, variables$measurement_models), "cumulative1991", sep = "_"),
  paste(c(variables$death_rates, variables$measurement_models), "cumulative1996", sep = "_"),
  paste(variables$conflict_incidence, "cumulative1991", sep = "_"),
  paste(variables$conflict_incidence, "cumulative1996", sep = "_"),
  paste(variables$political, "cumulative1991", sep = "_"),
  paste(variables$political, "cumulative1996", sep = "_"))]
names(new1990)[names(new1990) != "country"] <- paste(names(new1990)[names(new1990) != "country"], "1990", sep = "_")
names(new1995)[names(new1995) != "country"] <- paste(names(new1995)[names(new1995) != "country"], "1995", sep = "_")
names(new2015)[names(new2015) != "country"] <- paste(names(new2015)[names(new2015) != "country"], "2015", sep = "_")
new <- merge(new1990, new1995, by = c("country"), all = TRUE)
new <- merge(new, new2015, by = c("country"), all = TRUE)
## growth vars 
new$pc_rgdpe_avg_growth1990_2015      <- new$pc_rgdpe_pwt_avg_2015 - new$pc_rgdpe_pwt_avg_1990
new$pc_rgdpe_avg_growth1995_2015      <- new$pc_rgdpe_pwt_avg_2015 - new$pc_rgdpe_pwt_avg_1995
new$life_exp_wpp_avg_growth1990_2015  <- new$life_exp_wpp_avg_2015 - new$life_exp_wpp_avg_1990
new$life_exp_wpp_avg_growth1995_2015  <- new$life_exp_wpp_avg_2015 - new$life_exp_wpp_avg_1995
new$imr_wpp_avg_growth1990_2015       <- new$imr_wpp_avg_2015      - new$imr_wpp_avg_1990
new$imr_wpp_avg_growth1995_2015       <- new$imr_wpp_avg_2015      - new$imr_wpp_avg_1995
new$mys_ratio_hdr_avg_growth1990_2015 <- new$mys_ratio_hdr_avg_2015 - new$mys_ratio_hdr_avg_1990
new$mys_age_ratio_ihme_avg_growth1990_2015 <- new$mys_age_ratio_ihme_avg_2015 - new$mys_age_ratio_ihme_avg_1990
new$asfr_adol_wpp_avg_growth1990_2015      <- new$asfr_adol_wpp_avg_2015      - new$asfr_adol_wpp_avg_1990
new$asfr_adol_wpp_avg_growth1995_2015      <- new$asfr_adol_wpp_avg_2015      - new$asfr_adol_wpp_avg_1995
new$mys_ratio_hdr_avg_growth1995_2015      <- new$mys_ratio_hdr_avg_2015      - new$mys_ratio_hdr_avg_1995
new$mys_age_ratio_ihme_avg_growth1995_2015 <- new$mys_age_ratio_ihme_avg_2015 - new$mys_age_ratio_ihme_avg_1995
# summary(new[, c("mys_ratio_hdr_avg_growth1990_2015", "mys_ratio_hdr_avg_growth1995_2015", "mys_age_ratio_ihme_avg_growth1990_2015")])
## logged version of pcGDP growth vars; need to account for negative values
new$lg_pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 < 0)] <- log(-new$pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 < 0)])
new$lg_pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 >= 0)] <- log(new$pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 >= 0)])
new$lg_pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 < 0)] <- log(-new$pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 < 0)])
new$lg_pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 >= 0)] <- log(new$pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 >= 0)])
## performance versions of growth measures 
CodePerformance <- function(y_var, x_vars, show = FALSE, prefix = "perf") {
  x_vars <- paste(x_vars, collapse = " + ")
  equation <- paste(y_var, " ~ ", x_vars, sep = "")
  # print(equation)
  df <- na.omit(get_all_vars(formula = equation, data = new, country = country))
  mod <- lm(formula = equation, data = df)
  df$predicted <- predict(mod)
  df[, paste(prefix, y_var, sep = "_")] <- df[, y_var] - df$predicted
  if(show) print(df)
  return(invisible(df[, c("country", paste(prefix, y_var, sep = "_"))]))
}
vars <- c("life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "mys_age_ratio_ihme", "asfr_adol_wpp")
performance_measures <- unlist(lapply(c(1990, 1995), function(year) {
  unlist(lapply(paste(vars, "avg", sep = "_"), function(var) {
    return(list(
      CodePerformance(y_var = paste(var, "_growth", year, "_2015", sep = ""), 
                      x_vars = paste(c(str_replace(paste("lg", var, sep = "_"), "lg_mys", "mys"), "lg_pc_rgdpe_pwt_avg"), year, sep = "_")),
      CodePerformance(y_var = paste(var, "_growth", year, "_2015", sep = ""), 
                      x_vars = c(paste(c(str_replace(paste("lg", var, sep = "_"), "lg_mys", "mys"), "lg_pc_rgdpe_pwt_avg"), year, sep = "_"),
                                 paste("lg_pc_rgdpe_avg_growth", year, "_2015", sep = "")), prefix = "perfv2")
    ))
  }), recursive = FALSE)
}), recursive = FALSE)
performance_measures <- Reduce(f = function(...) merge(..., by = "country", all = TRUE), x = performance_measures)
new <- merge(new, performance_measures, by = "country", all = TRUE)
filepath <- "~/Dropbox/Lancet-SIGHT Commission/Working Groups/Metrics/Datasets/dataset_crosssectional.csv"
write.csv(new, file = filepath)
```

#### Performance Rankings within classification groups {.tabset .tabset-fade .tabset-pills}
```{r performance_function}
Performance <- function(category, year, vars) {
  countries <- unique(df$country[df$year == year & df$class_vv %in% category])
  countries <- countries[!is.na(countries)]
  lapply(vars, function(var) {
    var <- paste(var, "_growth", year, "_2015", sep = "")
    # other <- paste(c("deaths_all_ucdp_rate_cumulative"), year + 1, "_2015", sep = "")
    other <- NULL
    select_vars <- c("country", var, paste("perf", var, sep = "_"), other)
    # select_vars[!select_vars %in% names(new)]
    dat <- new[new$country %in% countries, select_vars]
    dat[order(dat[, var], decreasing = TRUE, na.last = NA), ]
  })
}
```

##### Low classification 
```{r performance_low}
Performance(category = "low", year = 1995, vars = paste(c(variables$health, variables$gender), "avg", sep = "_"))
```

##### H > G classification 
```{r performance_H}
Performance(category = "H>G", year = 1995, vars = paste(c(variables$health, variables$gender), "avg", sep = "_"))
```

##### G > H classification 
```{r performance_G}
Performance(category = "G>H", year = 1995, vars = paste(c(variables$health, variables$gender), "avg", sep = "_"))
```

##### High classification 
```{r performance_high}
Performance(category = "upp", year = 1995, vars = paste(c(variables$health, variables$gender), "avg", sep = "_"))
```

```{r saving}
save(data, codebook, categories, variables, df, new, file = "_data/LSCMWG_working_class.RData")
```
