---
title: "Classifications"
params: 
  cache: false
  optimize: true
---

```{r setup, include = FALSE}
source("setup.R")
```

```{r startup}
IsTrue <- function(x) { !is.na(x) & x }
load("_data/LSCMWG_working_data.RData")
```

### {.tabset .tabset-fade .tabset-pills}

#### Classification with two variables on each dimensions for 1990

```{r classification}
Classification <- function(health, gender, 
  df = data, 
  year_to_show = 1990, 
  min_to_include = 1
){
  qs <- paste("q", 1:5, sep = "") 
  vars = c(health, gender)
  df <- df[, c("country", "year", "period", vars)]
  ## creating 5-year averages
  df <- df %>% group_by(country, period) %>% 
    mutate(across(all_of(vars), ~mean(.x, na.rm = TRUE), .names = "{col}_avg"), .keep = "all")
  df <- df[df$year %in% c(seq(1965, 2015, 5), 2018), ]
  df <- df %>% group_by(year)
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), 
                      ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[2], .names = "{col}_q20"))
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), 
                      ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[3], .names = "{col}_q40"))
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), 
                      ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[4], .names = "{col}_q60"))
  df <- df %>% mutate(across(paste(vars, "avg", sep = "_"), 
                      ~quantile(.x, probs = seq(0, 1, 0.2), na.rm = TRUE)[5], .names = "{col}_q80"))
  df <- ungroup(df)

  df[, paste(vars, "quintile", sep = "_")] <- parallel::mclapply(vars, function(var) {
    col <- rep(NA, nrow(df))
    col[df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q20", sep = "_")]] <- 1
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q20", sep = "_")] & 
      df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q40", sep = "_")]] <- 2
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q40", sep = "_")] &
      df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q60", sep = "_")]] <- 3
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q60", sep = "_")] &
      df[, paste(var, "avg", sep = "_")] < df[, paste(var, "avg_q80", sep = "_")]] <- 4
    col[df[, paste(var, "avg", sep = "_")] >= df[, paste(var, "avg_q80", sep = "_")]] <- 5
    return(col)
  })
# df <- df[, c("country", "year", "period", names(df)[str_detect(names(df), fixed("quintile"))])]
  # combis <- expand.grid(health = health, gender = gender, stringsAsFactors = FALSE)
  # combis <- split(combis, seq(nrow(combis)))
  df$health_q1 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 1, na.rm = TRUE)
  df$health_q2 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 2, na.rm = TRUE)
  df$health_q3 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 3, na.rm = TRUE)
  df$health_q4 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 4, na.rm = TRUE) 
  df$health_q5 <- rowSums(df[, paste(health, "quintile", sep = "_")] == 5, na.rm = TRUE) 
  df$gender_q1 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 1, na.rm = TRUE) 
  df$gender_q2 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 2, na.rm = TRUE) 
  df$gender_q3 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 3, na.rm = TRUE) 
  df$gender_q4 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 4, na.rm = TRUE) 
  df$gender_q5 <- rowSums(df[, paste(gender, "quintile", sep = "_")] == 5, na.rm = TRUE)
  health_vars <- paste("health", qs, sep = "_")
  gender_vars <- paste("gender", qs, sep = "_")
  df$health_valid <- rowSums(df[, health_vars])
  df$gender_valid <- rowSums(df[, gender_vars])
  df$valid <- df$health_valid * df$gender_valid
  # unique(df$country[df$valid  == 0])
  df <- df[df$valid > 0, ]
  df <- df[, !names(df) %in% unlist(lapply(c("q20", "q40", "q60", "q80", "quintile", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp"), function(x) names(df)[str_detect(names(df), x)]))]
  # df <- df[, !names(df) %in% c("life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")]
  health_true <- df[, health_vars] == apply(df[, health_vars], MARGIN = 1, FUN = max)
  gender_true <- df[, gender_vars] == apply(df[, gender_vars], MARGIN = 1, FUN = max)
  health_help <- health_true * matrix(1:5, nrow = nrow(health_true), ncol = 5, byrow = TRUE)
  gender_help <- gender_true * matrix(1:5, nrow = nrow(gender_true), ncol = 5, byrow = TRUE)
  help_floor <- function(set) { return(floor(mean(set[set != 0]))) }
  help_ceiling <- function(set) { return(ceiling(mean(set[set != 0]))) }
  df$health_class <- apply(health_help, MARGIN = 1, help_floor)
  df$gender_class <- apply(gender_help, MARGIN = 1, help_floor)
  df$health_class_alt <- apply(health_help, MARGIN = 1, help_ceiling)
  df$gender_class_alt <- apply(gender_help, MARGIN = 1, help_ceiling)
  df$health_flag <- ifelse(df$health_class != df$health_class_alt, 1, 0)
  df$gender_flag <- ifelse(df$gender_class != df$gender_class_alt, 1, 0)
  health_index <- paste("health_q", df$health_class, sep = "")
  gender_index <- paste("gender_q", df$gender_class, sep = "")
  df$health_n <- unlist(lapply(1:length(health_index), function(index) { 
    as.integer(df[index, health_index[index]]) 
  }))
  df$gender_n <- unlist(lapply(1:length(gender_index), function(index) { 
    as.integer(df[index, gender_index[index]]) 
  }))
  df$combi <- df$health_n * df$gender_n
  df$class <- paste("H", df$health_class, "G", df$gender_class, sep = "")
  df$class_alt <- paste("H", df$health_class_alt, "G", df$gender_class_alt, sep = "")
  df$class_num <-df$health_class * df$gender_class
  test <- table(df[df$year == year_to_show & df$valid >= min_to_include, c("health_class", "gender_class")])
  print(test)
  number_of_countries <- sum(test)
  df$support <- paste(df$country, " (", df$combi, "/", df$valid, ")", sep = "")
  dat <- df[df$year == year_to_show, ]
  table_to_return <- tapply(dat$support, 
                            INDEX = list(health = dat$health_class, gender = dat$gender_class), 
                            paste, collapse = "; ")
  table_to_return[is.na(table_to_return)] <- ""
  dimnames(table_to_return) <- lapply(dimnames(table_to_return), function(name) { paste("Q", name, sep = "") })
  ## from here, this is the old way, to create the fuzzy table, not needed anymore but useful for comparison
  df$H1G1 <- df$health_q1 * df$gender_q1
  df$H2G1 <- df$health_q2 * df$gender_q1
  df$H3G1 <- df$health_q3 * df$gender_q1
  df$H4G1 <- df$health_q4 * df$gender_q1
  df$H5G1 <- df$health_q5 * df$gender_q1
  df$H1G2 <- df$health_q1 * df$gender_q2
  df$H2G2 <- df$health_q2 * df$gender_q2
  df$H3G2 <- df$health_q3 * df$gender_q2
  df$H4G2 <- df$health_q4 * df$gender_q2
  df$H5G2 <- df$health_q5 * df$gender_q2
  df$H1G3 <- df$health_q1 * df$gender_q3
  df$H2G3 <- df$health_q2 * df$gender_q3
  df$H3G3 <- df$health_q3 * df$gender_q3
  df$H4G3 <- df$health_q4 * df$gender_q3
  df$H5G3 <- df$health_q5 * df$gender_q3
  df$H1G4 <- df$health_q1 * df$gender_q4
  df$H2G4 <- df$health_q2 * df$gender_q4
  df$H3G4 <- df$health_q3 * df$gender_q4
  df$H4G4 <- df$health_q4 * df$gender_q4
  df$H5G4 <- df$health_q5 * df$gender_q4
  df$H1G5 <- df$health_q1 * df$gender_q5
  df$H2G5 <- df$health_q2 * df$gender_q5
  df$H3G5 <- df$health_q3 * df$gender_q5
  df$H4G5 <- df$health_q4 * df$gender_q5
  df$H5G5 <- df$health_q5 * df$gender_q5
  vars <- c("H1G1", "H2G1", "H3G1", "H4G1", "H5G1", 
            "H1G2", "H2G2", "H3G2", "H4G2", "H5G2", 
            "H1G3", "H2G3", "H3G3", "H4G3", "H5G3", 
            "H1G4", "H2G4", "H3G4", "H4G4", "H5G4", 
            "H1G5", "H2G5", "H3G5", "H4G5", "H5G5")
  names(vars) <- vars
  dat <- as.data.frame(df[df$year == year_to_show, c("country", "valid", vars)])
  classifications <- parallel::mclapply(vars, function(var_name) {
    new <- dat[dat[, var_name] >= min_to_include, c("country", var_name, "valid")]
    countries <- new$country
    new <- paste(new[, "country"], " (", new[, var_name], "/", new[, "valid"], ")", sep = "")
    new <- new[new != " (/)"]    
    return(list(class = new, ctry = countries))
  })
  countries <- sort(unique(unlist(lapply(classifications, function(x) { x$ctry }))))
  classifications <- lapply(classifications, function(class) { class$class })
  classifications <- lapply(classifications, paste, collapse = "; ")
  # print(matrix(names(classifications), 5, 5, dimnames = list(health = qs, gender = qs)))
  fuzzy_table <- matrix(classifications, 5, 5, dimnames = list(health = qs, gender = qs))
  cat("Number of countries classified: ", number_of_countries, "\n")
  if(number_of_countries != length(countries)) {
    cat("\nNot classifying the same number of countries as the old way!")
  }
  df <- df[, !names(df) %in% vars]
  return(list(df = df, n = number_of_countries, table = table_to_return, fuzzy = fuzzy_table))  
}
result <- Classification(health = variables$health, gender = variables$gender)
kableExtra::kable(result$table, format = "html") %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::add_header_above(c(" " = 1, "Gender" = 5)) %>% 
  kableExtra::group_rows("Health", 1, 5)
```

```{r toy, echo = FALSE, eval = FALSE}
temp <- expand.grid(health = paste("H", 1:5, sep = ""), gender = paste("G", 1:5, sep = ""))
temp$cell <- paste(temp$health, temp$gender, sep = "")
tapply(temp$cell, INDEX = list(health = temp$health, gender = temp$gender), I)
```

#### Fuzzy version of classification (for illustration only)
```{r fuzzy}
kableExtra::kable(result$fuzzy, format = "html") %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::add_header_above(c(" " = 1, "Gender" = 5)) %>% 
  kableExtra::group_rows("Health", 1, 5)
```

<!-- ### Classification using the performance versions of the health and gender inputs -->
```{r perf, eval = FALSE, echo = FALSE}
result_perf <- Classification(health = paste("perf", variables$health, sep = "_"), 
                              gender = paste("perf", variables$gender, sep = "_"), year_to_show = 1995)
kableExtra::kable(result_perf$table, format = "html") %>% 
  kableExtra::kable_styling("striped") %>% 
  kableExtra::add_header_above(c(" " = 1, "Gender" = 5)) %>% 
  kableExtra::group_rows("Health", 1, 5)
```

#### Merging classifications into dataset

```{r merging}
variables$class <- c("health_valid", "gender_valid", "health_class", "gender_class", 
                     "health_class_alt", "gender_class_alt", "health_flag", "gender_flag", 
                     "health_n", "gender_n", "class", "class_alt", "support")
df <- as.data.frame(result$df[, c("country", "year", "period", "class_num", variables$class)])
flagged <- df[df$year == 1990 & (df$health_flag == 1 | df$gender_flag == 1), 
              c("country", "class_num", variables$class)]
df$class_vv <- NA
df$class_vv[df$health_class < 3 & df$gender_class < 3] <- "low"
df$class_vv[df$health_class > 3 & df$gender_class > 3] <- "upp"
df$class_vv[!(df$health_class < 3 & df$gender_class < 3) & !(df$health_class > 3 & df$gender_class > 3)] <- "mid"
df$class_vv[df$class_vv == "mid" & df$health_class > df$gender_class] <- "H>G"
df$class_vv[df$class_vv == "mid" & df$health_class < df$gender_class] <- "G>H"
## alt
df$class_vv_alt <- NA
df$class_vv_alt[df$health_class_alt < 3 & df$gender_class_alt < 3] <- "low"
df$class_vv_alt[df$health_class_alt > 3 & df$gender_class_alt > 3] <- "upp"
df$class_vv_alt[!(df$health_class_alt < 3 & df$gender_class_alt < 3) & !(df$health_class_alt > 3 & df$gender_class_alt > 3)] <- "mid"
df$class_vv_alt[df$class_vv_alt == "mid" & df$health_class_alt > df$gender_class_alt] <- "H>G"
df$class_vv_alt[df$class_vv_alt == "mid" & df$health_class_alt < df$gender_class_alt] <- "G>H"
# addmargins(table(df$class_vv, df$class))
df$class_low <- ifelse(df$class_vv == "low", 1, 0)
df$class_upp <- ifelse(df$class_vv == "upp", 1, 0)
df$class_mid <- ifelse(df$class_vv == "mid", 1, 0)
df$class_HG <- ifelse(df$class_vv == "H>G", 1, 0)
df$class_GH <- ifelse(df$class_vv == "G>H", 1, 0)
variables$class_core <- c("country", "class", "health_class", "gender_class", "class_vv")
class1990 <- df[df$year == 1990, variables$class_core]
names(class1990) <- c("country", paste(c("class", "health", "gender", "class_vv"), 1990, sep = ""))
class1995 <- df[df$year == 1995, variables$class_core]
names(class1995) <- c("country", paste(c("class", "health", "gender", "class_vv"), 1995, sep = ""))
df <- merge(data, df[, names(df) != "year"], by = c("country", "period"), all = TRUE)
df <- merge(df, class1990, by = "country", all.x = TRUE)
df <- merge(df, class1995, by = "country", all.x = TRUE)
df <- df[order(df$country, df$year), 
         c("country", "year", "period", names(df)[!names(df) %in% c("country", "year", "period")])]
df <- df[df$year != 1960 & df$year != 2019, ]
filepath <- paste("~/Dropbox/Lancet-SIGHT Commission/Working Groups/Metrics/Datasets/dataset_cy_class", ".csv", sep = "" )
write_csv(df, file = filepath)
```

#### Subset of 1990 classifications for which "floor" rule was applied
```{r flagged}
flagged
```

<!-- ### Classification trajectories (in 5-year increments based on global distributions in same time period) -->
```{r class_time, echo = FALSE, eval = FALSE, message = FALSE, fig.width = 14, fig.height = 10, out.width = "100%", out.height = "100%"}
ggplot(data = df[df$year %in% seq(1965, 2015, 5), ]) + 
  geom_line(aes(x = year, y = class_num)) + 
  facet_wrap(~country) +
  theme_classic() + 
  scale_x_continuous(breaks = seq(1970, 2010, by = 20))
```

<!-- ### Descriptives of control variables by 1990 classification: mean (SD) [currently not shown] -->
```{r descriptives, echo = FALSE, eval = FALSE}
Descriptives <- function(cell, digits = 2) {
  mean <- mean(cell, na.rm = TRUE)
  sd <- sd(cell, na.rm = TRUE)
  ifelse(!is.na(mean), paste(round(mean, digits), " (", round(sd, digits), ")", sep = ""), "")
}
table_to_show <- lapply(variables$controls, function(var) {
  to_return <- tapply(df[, var], 
                      INDEX = list(health = df$health1990, gender = df$gender1990), 
                      FUN =  Descriptives)
  to_return[is.na(to_return)] <- ""
  return(to_return)
})
noquote(table_to_show)
```

#### Which countries move more than 2 cells?
```{r movers}
names(years) <- years <- c(1990, 1995, 2015)
dat <- lapply(years, function(year) {
  df <- as.data.frame(df[df$year == year, c("country", "class_num")])
  names(df)[2] <- paste("class", year, sep = "")
  return(df)
})
dat <- Reduce(f = function(...) merge(..., by = "country", all = TRUE), x = dat)
dat$diff <- dat$class2015 - dat$class1990
dat$diff_alt <- dat$class2015 - dat$class1995
better <- dat[IsTrue(dat$diff > 2 | dat$diff_alt > 2), ]
worse <- dat[IsTrue(dat$diff < -2 | dat$diff_alt < -2), ]
better 
worse
```

#### Removing countries with untrustworthy statistics 

All data is subject to measurement error. This is particularly problematic if measurement is systematically biased. Without other data to validate a given measure, this is a very difficult to problem to overcome. We only use data from reputable sources, such as academic centre and international organizations, but some self-reported data are still suspect. The World Bank and some NGOs have attempted to rate the capacity of National Statistical System, and some countries are not inlcuded in their rankings because assessments could be not be made based on available information. For instance, the ODIN rankings from 2015 to 2018 do not include the Central African Republic, Eritrea, Equatorial Guinea, and North Korea. Interestingly, among these, only North Korea is relatively highly ranked on the gender and health dimensions according to these data, which is simply not believable. Therefore, we remove only North Korea from the analyses.

```{r capacity}
df <- df[df$country != "North Korea", ]
```

#### Trends by classification groups over time {.tabset .tabset-fade .tabset-pills}

```{r trends}
### making trend figures for the Dec 9 presentation
df_new <- df[df$year %in% 1965:2018, 
             c("country", "year", "class_vv", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")]
df_new <- df_new %>% group_by(year) %>% mutate(avg_life_exp_wpp = mean(life_exp_wpp, na.rm = TRUE))
df_new <- df_new %>% group_by(year) %>% mutate(avg_imr_wpp = -mean(imr_wpp, na.rm = TRUE))
df_new <- df_new %>% group_by(year) %>% mutate(avg_mys_ratio_hdr = mean(mys_ratio_hdr, na.rm = TRUE))
df_new <- df_new %>% group_by(year) %>% mutate(avg_asfr_adol_wpp = -mean(asfr_adol_wpp, na.rm = TRUE))
df_new <- unique(df_new[, c("year", "avg_life_exp_wpp", "avg_imr_wpp", "avg_mys_ratio_hdr", "avg_asfr_adol_wpp")])
df_low <- df[df$year %in% 1965:2018 & df$class_vv == "low", 
             c("country", "year", "class_vv", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")]
df_low <- df_low %>% group_by(year) %>% mutate(low_life_exp_wpp = mean(life_exp_wpp, na.rm = TRUE))
df_low <- df_low %>% group_by(year) %>% mutate(low_imr_wpp = -mean(imr_wpp, na.rm = TRUE))
df_low <- df_low %>% group_by(year) %>% mutate(low_mys_ratio_hdr = mean(mys_ratio_hdr, na.rm = TRUE))
df_low <- df_low %>% group_by(year) %>% mutate(low_asfr_adol_wpp = -mean(asfr_adol_wpp, na.rm = TRUE))
df_low <- unique(df_low[, c("year", "low_life_exp_wpp", "low_imr_wpp", "low_mys_ratio_hdr", "low_asfr_adol_wpp")])
df_upp <- df[df$year %in% 1965:2018 & df$class_vv == "upp", 
             c("country", "year", "class_vv", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")]
df_upp <- df_upp %>% group_by(year) %>% mutate(upp_life_exp_wpp = mean(life_exp_wpp, na.rm = TRUE))
df_upp <- df_upp %>% group_by(year) %>% mutate(upp_imr_wpp = -mean(imr_wpp, na.rm = TRUE))
df_upp <- df_upp %>% group_by(year) %>% mutate(upp_mys_ratio_hdr = mean(mys_ratio_hdr, na.rm = TRUE))
df_upp <- df_upp %>% group_by(year) %>% mutate(upp_asfr_adol_wpp = -mean(asfr_adol_wpp, na.rm = TRUE))
df_upp <- unique(df_upp[, c("year", "upp_life_exp_wpp", "upp_imr_wpp", "upp_mys_ratio_hdr", "upp_asfr_adol_wpp")])
df_mid <- df[df$year %in% 1965:2018 & df$class_vv == "mid", 
             c("country", "year", "class_vv", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")]
df_mid <- df_mid %>% group_by(year) %>% mutate(mid_life_exp_wpp = mean(life_exp_wpp, na.rm = TRUE))
df_mid <- df_mid %>% group_by(year) %>% mutate(mid_imr_wpp = -mean(imr_wpp, na.rm = TRUE))
df_mid <- df_mid %>% group_by(year) %>% mutate(mid_mys_ratio_hdr = mean(mys_ratio_hdr, na.rm = TRUE))
df_mid <- df_mid %>% group_by(year) %>% mutate(mid_asfr_adol_wpp = -mean(asfr_adol_wpp, na.rm = TRUE))
df_mid <- unique(df_mid[, c("year", "mid_life_exp_wpp", "mid_imr_wpp", "mid_mys_ratio_hdr", "mid_asfr_adol_wpp")])
df_Hlop <- df[df$year %in% 1965:2018 & df$class_vv == "H>G", 
             c("country", "year", "class_vv", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")]
df_Hlop <- df_Hlop %>% group_by(year) %>% mutate(HG_life_exp_wpp = mean(life_exp_wpp, na.rm = TRUE))
df_Hlop <- df_Hlop %>% group_by(year) %>% mutate(HG_imr_wpp = -mean(imr_wpp, na.rm = TRUE))
df_Hlop <- df_Hlop %>% group_by(year) %>% mutate(HG_mys_ratio_hdr = mean(mys_ratio_hdr, na.rm = TRUE))
df_Hlop <- df_Hlop %>% group_by(year) %>% mutate(HG_asfr_adol_wpp = -mean(asfr_adol_wpp, na.rm = TRUE))
df_Hlop <- unique(df_Hlop[, c("year", "HG_life_exp_wpp", "HG_imr_wpp", "HG_mys_ratio_hdr", "HG_asfr_adol_wpp")])
df_Glop <- df[df$year %in% 1965:2018 & df$class_vv == "G>H", 
             c("country", "year", "class_vv", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")]
df_Glop <- df_Glop %>% group_by(year) %>% mutate(GH_life_exp_wpp = mean(life_exp_wpp, na.rm = TRUE))
df_Glop <- df_Glop %>% group_by(year) %>% mutate(GH_imr_wpp = -mean(imr_wpp, na.rm = TRUE))
df_Glop <- df_Glop %>% group_by(year) %>% mutate(GH_mys_ratio_hdr = mean(mys_ratio_hdr, na.rm = TRUE))
df_Glop <- df_Glop %>% group_by(year) %>% mutate(GH_asfr_adol_wpp = -mean(asfr_adol_wpp, na.rm = TRUE))
df_Glop <- unique(df_Glop[, c("year", "GH_life_exp_wpp", "GH_imr_wpp", "GH_mys_ratio_hdr", "GH_asfr_adol_wpp")])
df_new <- merge(df_new, df_low, by = "year", all = TRUE)
df_new <- merge(df_new, df_mid, by = "year", all = TRUE)
df_new <- merge(df_new, df_Hlop, by = "year", all = TRUE)
df_new <- merge(df_new, df_Glop, by = "year", all = TRUE)
df_new <- merge(df_new, df_upp, by = "year", all = TRUE)
```

##### Life expectancy
```{r pdf_life, fig.width = 12, fig.height = 8}
# pdf(file = paste("_summary/trend_life_exp_wpp.pdf", sep = ""), width = 16, height = 9)
dat <- na.omit(df_new[, c("year", "avg_life_exp_wpp", "low_life_exp_wpp", "HG_life_exp_wpp", "GH_life_exp_wpp", "mid_life_exp_wpp", "upp_life_exp_wpp")])
matplot(x = dat$year, y = dat[, -1], type = "l", xlab = "", ylab = "", 
        main = "Life Expectancy", lwd = 2, lty = "solid", col = c("black", "red","orange", "purple", "green", "blue"))
legend("bottomright", legend = c("global average", "low classification", "H>G classification", "G>H classification", "mid classification", "high classification"), 
       lty = "solid", lwd = 2, col = c("black", "red","orange", "purple", "green", "blue"))
# dev.off()
```

##### IMR
```{r pdf_imr, fig.width = 12, fig.height = 8}
# pdf(file = paste("_summary/trend_imr_wpp.pdf", sep = ""), width = 16, height = 9)
dat <- na.omit(df_new[, c("year", "avg_imr_wpp", "low_imr_wpp", "HG_imr_wpp", "GH_imr_wpp", "mid_imr_wpp", "upp_imr_wpp")])
matplot(x = dat$year, y = dat[, -1], type = "l", xlab = "", ylab = "", 
        main = "Infant Mortality Rate", lwd = 2, lty = "solid", col = c("black", "red","orange", "purple", "green", "blue"))
legend("topright", legend = c("global average", "low classification", "H>G classification", "G>H classification", "mid classification", "high classification"), 
       lty = "solid", lwd = 2, col = c("black", "red","orange", "purple", "green", "blue"))
# dev.off()
```

##### MYS
```{r pdf_mys, fig.width = 12, fig.height = 8}
# pdf(file = paste("_summary/trend_mys_ratio_hdr.pdf", sep = ""), width = 16, height = 9)
dat <- na.omit(df_new[, c("year", "avg_mys_ratio_hdr", "low_mys_ratio_hdr", "HG_mys_ratio_hdr", "GH_mys_ratio_hdr", "mid_mys_ratio_hdr", "upp_mys_ratio_hdr")])
matplot(x = dat$year, y = dat[, -1], type = "l", xlab = "", ylab = "", 
        main = "Mean Years of Schooling", lwd = 2, lty = "solid", col = c("black", "red","orange", "purple", "green", "blue"))
legend("bottomright", legend = c("global average", "low classification", "H>G classification", "G>H classification", "mid classification", "high classification"), 
       lty = "solid", lwd = 2, col = c("black", "red","orange", "purple", "green", "blue"))
# dev.off()
```

##### ASFR
```{r pdf_asfr, fig.width = 12, fig.height = 8}
# pdf(file = paste("_summary/trend_asfr_adol_wpp.pdf", sep = ""), width = 16, height = 9)
dat <- na.omit(df_new[, c("year", "avg_asfr_adol_wpp", "low_asfr_adol_wpp", "HG_asfr_adol_wpp", "GH_asfr_adol_wpp", "mid_asfr_adol_wpp", "upp_asfr_adol_wpp")])
matplot(x = dat$year, y = dat[, -1], type = "l", xlab = "", ylab = "", 
        main = "Adolescent Fertility Rate", lwd = 2, lty = "solid", col = c("black", "red","orange", "purple", "green", "blue"))
legend("topright", legend = c("global average", "low classification", "H>G classification", "G>H classification", "mid classification", "high classification"), 
       lty = "solid", lwd = 2, col = c("black", "red","orange", "purple", "green", "blue"))
# dev.off()
```

#### Trends by 1995 classification groups {.tabset .tabset-fade .tabset-pills}

##### Health & gender
```{r categories, message = FALSE, results = 'hide'}
summary(as.factor(df$class_vv1990))
summary(as.factor(df$class_vv1995))
lapply(c(variables$health_full, variables$gender_full), function(var) {
  dat <- df[!is.na(df$class_vv1995) & df$class_vv1995 != "mid", ]
  ggplot(dat, aes(x = year, y = !!sym(var), group = class_vv1995, color = class_vv1995)) + 
    stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
    xlim(1980, 2018) + 
    theme_bw() + 
    ggtitle(paste(var, "average by 1995 classification over time"))
})
```

##### Cumulative death rates
```{r deaths, message = FALSE, results = 'hide'}
lapply(variables$death_rates, function(var) {
  dat <- df[!is.na(df$class_vv1995) & df$class_vv1995 != "mid", ]
  ggplot(dat, aes(x = year, y = log(!!sym(paste(var, "cumulative1991", sep = "_")) + 1), 
                  group = class_vv1995, color = class_vv1995)) + 
    stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
    xlim(1990, 2018) + 
    theme_bw() + 
    ggtitle(paste(var, "annual cumulative average (logged) since 1991 by 1995 classification"))
})
```

##### Cumulative repression
```{r violence, message = FALSE, results = 'hide'}
lapply(variables$measurement_models, function(var) {
  dat <- df[!is.na(df$class_vv1995) & df$class_vv1995 != "mid", ]
  ggplot(dat, aes(x = year, y = !!sym(paste(var, "cumulative1991", sep = "_")), 
                  group = class_vv1995, color = class_vv1995)) + 
  stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
  xlim(1990, 2018) + 
  theme_bw() + 
  ggtitle(paste(var, "annual cumulative average since 1991 by 1995 classification"))
})
```

##### Conflict incidence

```{r incidence, message = FALSE, warning = FALSE, results = 'hide'}
lapply(variables$conflict_incidence, function(var) {
  dat <- df[df$year > 1988, ]
  tbl <- tapply(dat[, var], list(health = dat$health1995, gender = dat$gender1995), mean, na.rm = TRUE)
  dat <- dat[!is.na(dat$class_vv1995) & dat$class_vv1995 != "mid", ]
  plot <- ggplot(dat, aes(x = year, y = !!sym(var), group = class_vv1995, color = class_vv1995)) + 
    stat_summary(fun="mean", geom="line", na.rm = TRUE, size = 1) + 
    xlim(1989, 2018) + 
    theme_bw() + 
    ggtitle(paste(var, " incidence by classification in 1995"))
  return(list(tbl, plot))
})
```

<!-- #### Mean growth rates by classification with t-test (alt H: mean different from global) -->
```{r growth_rates, echo = FALSE, eval = FALSE}
GrowthRatesTtest <- function(var, min_obs = 2) { 
  dat1995 <- df[df$year == 1995, c("country", "class", "health_class", "gender_class", var)]
  dat2015 <- df[df$year == 2015, c("country", var)]
  names(dat1995)[names(dat1995) != "country"] <- paste(names(dat1995)[names(dat1995) != "country"] , 
                                                       1995, sep = "_")
  names(dat2015)[names(dat2015) != "country"] <- paste(names(dat2015)[names(dat2015) != "country"] , 
                                                       2015, sep = "_")
  dat <- merge(dat1995, dat2015, by = c("country"), all = TRUE)
  dat$growth <- dat[, paste(var, 2015, sep ="_")] - dat[, paste(var, 1995, sep ="_")]
  tbl <- tapply(dat$growth, list(health = dat$health_class_1995, gender = dat$gender_class_1995), function(df) {
    if(sum(!is.na(df)) >= min_obs) {
      result <- t.test(df, mu = mean(dat$growth, na.rm = TRUE))
      mean <- round(result[["estimate"]][["mean of x"]], 2)
      pvalue <- round(result[["p.value"]], 2)
      df <- result[["parameter"]][["df"]]
      cell <- paste(mean, " (p-value ", pvalue, "; df ", df, ")", sep = "")
    } else { cell <- "" }
    return(cell)
  })
  tbl[is.na(tbl)] <- ""
  return(list(global_mean = mean(dat$growth, na.rm = TRUE), ttests = noquote(tbl)))
}
variables$outcomes <- c(variables$health_full, variables$gender_full, variables$death_rates, variables$measurement_models)
parallel::mclapply(variables$outcomes, GrowthRatesTtest)
```

#### Preparing cross-sectional dataset
```{r reg_prep}
covariates <- c("pc_rgdpe_pwt", "life_exp_wpp", "imr_wpp", "mys_ratio_hdr", "asfr_adol_wpp")
covariates <- c(covariates, "oda_provided_const_wdi", "oda_received_perc_gov_exp_wdi", "oda_aid_received_const_wdi", "oda_received_const_wdi", "oda_received_perc_imports_wdi", "aid_received_const_wdi")
vars <- unlist(lapply(covariates, function(var) { names(df)[str_detect(names(df), var)] }))
vars <- unique(vars[vars != "pasfr_adol_wpp"])
include <- c("country", "class", "class_vv", "class_low", "class_upp", vars)
new1990 <- df[df$year == 1990, c(include, variables$death_rates, variables$measurement_models)]
new1995 <- df[df$year == 1995, c(include, variables$death_rates, variables$measurement_models, 
  paste(variables$conflict_incidence, "cumulative1989", sep = "_"),
  paste(variables$political, "cumulative1991", sep = "_"))]
new2015 <- df[df$year == 2015, c(include, 
  paste(c(variables$death_rates, variables$measurement_models), "cumulative1991", sep = "_"),
  paste(c(variables$death_rates, variables$measurement_models), "cumulative1996", sep = "_"),
  paste(variables$conflict_incidence, "cumulative1991", sep = "_"),
  paste(variables$conflict_incidence, "cumulative1996", sep = "_"),
  paste(variables$political, "cumulative1991", sep = "_"),
  paste(variables$political, "cumulative1996", sep = "_"))]
names(new1990)[names(new1990) != "country"] <- paste(names(new1990)[names(new1990) != "country"], "1990", sep = "_")
names(new1995)[names(new1995) != "country"] <- paste(names(new1995)[names(new1995) != "country"], "1995", sep = "_")
names(new2015)[names(new2015) != "country"] <- paste(names(new2015)[names(new2015) != "country"], "2015", sep = "_")
new <- merge(new1990, new1995, by = c("country"), all = TRUE)
new <- merge(new, new2015, by = c("country"), all = TRUE)
## growth vars 
new$pc_rgdpe_avg_growth1990_2015  <- new$pc_rgdpe_pwt_avg_2015 - new$pc_rgdpe_pwt_avg_1990
new$pc_rgdpe_avg_growth1995_2015  <- new$pc_rgdpe_pwt_avg_2015 - new$pc_rgdpe_pwt_avg_1995
new$life_exp_wpp_growth1990_2015  <- new$life_exp_wpp_2015     - new$life_exp_wpp_1990
new$life_exp_wpp_avg_growth1990_2015  <- new$life_exp_wpp_avg_2015     - new$life_exp_wpp_avg_1990
new$life_exp_wpp_growth1995_2015  <- new$life_exp_wpp_2015     - new$life_exp_wpp_1995
new$life_exp_wpp_avg_growth1995_2015  <- new$life_exp_wpp_avg_2015     - new$life_exp_wpp_avg_1995
new$imr_wpp_growth1990_2015       <- new$imr_wpp_2015          - new$imr_wpp_1990
new$imr_wpp_avg_growth1990_2015       <- new$imr_wpp_avg_2015          - new$imr_wpp_avg_1990
new$imr_wpp_growth1995_2015       <- new$imr_wpp_2015          - new$imr_wpp_1995
new$imr_wpp_avg_growth1995_2015       <- new$imr_wpp_avg_2015          - new$imr_wpp_avg_1995
new$mys_ratio_hdr_growth1990_2015 <- new$mys_ratio_hdr_2015    - new$mys_ratio_hdr_1990
new$mys_ratio_hdr_avg_growth1990_2015 <- new$mys_ratio_hdr_avg_2015    - new$mys_ratio_hdr_avg_1990
new$asfr_adol_wpp_growth1990_2015 <- new$asfr_adol_wpp_2015    - new$asfr_adol_wpp_1990
new$asfr_adol_wpp_avg_growth1990_2015 <- new$asfr_adol_wpp_avg_2015    - new$asfr_adol_wpp_avg_1990
new$asfr_adol_wpp_growth1995_2015 <- new$asfr_adol_wpp_2015    - new$asfr_adol_wpp_1995
new$asfr_adol_wpp_avg_growth1995_2015 <- new$asfr_adol_wpp_avg_2015    - new$asfr_adol_wpp_avg_1995
new$mys_ratio_hdr_growth1995_2015 <- new$mys_ratio_hdr_2015    - new$mys_ratio_hdr_1995
new$mys_ratio_hdr_avg_growth1995_2015 <- new$mys_ratio_hdr_avg_2015    - new$mys_ratio_hdr_avg_1995
summary(new[, c("mys_ratio_hdr_growth1990_2015", "mys_ratio_hdr_avg_growth1990_2015")])
summary(new[, c("mys_ratio_hdr_growth1995_2015", "mys_ratio_hdr_avg_growth1995_2015")])
## logged version of pcGDP growth vars; need to account for negative values
new$lg_pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 < 0)] <- log(-new$pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 < 0)])
new$lg_pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 >= 0)] <- log(new$pc_rgdpe_avg_growth1990_2015[IsTrue(new$pc_rgdpe_avg_growth1990_2015 >= 0)])
new$lg_pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 < 0)] <- log(-new$pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 < 0)])
new$lg_pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 >= 0)] <- log(new$pc_rgdpe_avg_growth1995_2015[IsTrue(new$pc_rgdpe_avg_growth1995_2015 >= 0)])
## performance versions of growth measures 
CodePerformance <- function(y_var, x_vars, show = FALSE, prefix = "perf") {
  x_vars <- paste(x_vars, collapse = " + ")
  equation <- paste(y_var, " ~ ", x_vars, sep = "")
  df <- na.omit(get_all_vars(formula = equation, data = new, country = country))
  mod <- lm(formula = equation, data = df)
  df$predicted <- predict(mod)
  df[, paste(prefix, y_var, sep = "_")] <- df[, y_var] - df$predicted
  if(show) print(df)
  return(invisible(df[, c("country", paste(prefix, y_var, sep = "_"))]))
}
performance_measures <- unlist(lapply(c(1990, 1995), function(year) {
  unlist(lapply(c(covariates[2:5], paste(covariates[2:5], "avg", sep = "_")), function(var) {
    return(list(
      CodePerformance(y_var = paste(var, "_growth", year, "_2015", sep = ""), 
                      x_vars = paste(c(paste("lg", var, sep = "_"), "lg_pc_rgdpe_pwt_avg"), year, sep = "_")),
      CodePerformance(y_var = paste(var, "_growth", year, "_2015", sep = ""), 
                      x_vars = c(paste(c(paste("lg", var, sep = "_"), "lg_pc_rgdpe_pwt_avg"), year, sep = "_"),
                                 paste("lg_pc_rgdpe_avg_growth", year, "_2015", sep = "")), prefix = "perfv2")
    ))
  }), recursive = FALSE)
}), recursive = FALSE)
performance_measures <- Reduce(f = function(...) merge(..., by = "country", all = TRUE), x = performance_measures)
new <- merge(new, performance_measures, by = "country", all = TRUE)
filepath <- paste("~/Dropbox/Lancet-SIGHT Commission/Working Groups/Metrics/Datasets/dataset_crosssectional", ".csv", sep = "" )
write.csv(new, file = filepath)
```

#### Performance Rankings within classification groups {.tabset .tabset-fade .tabset-pills}

```{r performance_function, message = FALSE, warning = FALSE}
Performance <- function(category, year, vars) {
  countries <- unique(df$country[df$year == year & df$class_vv %in% category])
  countries <- countries[!is.na(countries)]
  lapply(vars, function(var) {
    var <- paste(var, "_growth", year, "_2015", sep = "")
    # other <- paste(c("deaths_all_ucdp_rate_cumulative"), year + 1, "_2015", sep = "")
    other <- NULL
    select_vars <- c("country", var, paste("perf", var, sep = "_"), other)
    # select_vars[!select_vars %in% names(new)]
    dat <- new[new$country %in% countries, select_vars]
    dat[order(dat[, var], decreasing = TRUE, na.last = NA), ]
  })
}
```

##### Low classification 
```{r performance_low}
Performance(category = "low", year = 1995, vars = c(variables$health, variables$gender))
```

##### H > G classification 
```{r performance_H}
Performance(category = "H>G", year = 1995, vars = c(variables$health, variables$gender))
```

##### G > H classification 
```{r performance_G}
Performance(category = "G>H", year = 1995, vars = c(variables$health, variables$gender))
```

##### High classification 
```{r performance_high}
Performance(category = "upp", year = 1995, vars = c(variables$health, variables$gender))
```

```{r saving}
save(data, codebook, categories, variables, df, new, file = "_data/LSCMWG_working_class.RData")
```
