---
title: "Panel Regressions"
params: 
  cache: true
  optimize: false
  lags: 1
  begin: 1965
  end: 2018
---

```{r setup, include = FALSE}
source("setup.R")
library(plm)
knitr::opts_chunk$set(fig.width = 12, fig.height = 12, rows.print = 15, cols.min.print = 5, out.width = "100%", out.height = "100%")
```

```{r prelim}
IsTrue <- function(x) { !is.na(x) & x }
load("_data/LSCMWG_working_class.RData")
vars <- c("pc_rgdpe_pwt", "pop_wpp", unlist(variables[c("health_full", "gender_full", "conflict_incidence", 
                                                        "death_rates", "measurement_models", "political")], 
                                            use.names = FALSE), 
          paste("perf", unlist(variables[c("health", "gender")], use.names = FALSE), sep = "_"),
          "gdi_hdr", "gii_hdr", "mmr_unicef"          
          )
dfp <- df[, c("country", "year", "period", "health_class", "gender_class", 
              "class", "class_alt", "class_vv", "class_vv_alt", "class_low", "class_HG", "class_GH", "class_mid", "class_upp", vars)]
dfp <- dfp %>% dplyr::arrange(country, period, year)
dfp <- dfp %>% group_by(country, period) %>% 
  mutate(across(all_of(vars), ~mean(.x, na.rm = TRUE), .names = "{col}"), .keep = "all")
dfp[, vars] <- lapply(dfp[, vars], function(col) {
  col[is.nan(col)] <- NA
  return(col)
})
take_logs <- c("pc_rgdpe_pwt", "pop_wpp", "life_exp_wpp", "mys_ratio_hdr")
take_logs_negative <- c("imr_wpp", "ufmr_wpp", "daly_ihme", "asfr_adol_wpp")
dfp[, paste("lg", take_logs, sep = "_")] <- lapply(dfp[, take_logs], log)
dfp[, paste("lg", take_logs_negative, sep = "_")] <- lapply(dfp[, take_logs_negative], 
                                                            function(col) { -log(-col) })
# summary(dfp[, c(take_logs, take_logs_negative)])
viol_vars <- c("conflict_internal", "war_internal", "conflict_non_state", 
               "conflict_one_sided", "latentmean_fariss", "v2cltort", "v2clkill")
viol_vars_log <- c("deaths_all_int_rate", "deaths_civilians_int_rate", "deaths_civilians_osv_rate", 
                   "deaths_all_nsc_rate", "deaths_civilians_nsc_rate", "deaths_all_ucdp_rate", "hom_odcwho_rate")
dfp[, paste("lg", viol_vars_log, sep = "_")] <- lapply(dfp[, viol_vars_log], function(col) { log(col + 1) })
dfp$health_class_low <- NA
dfp$health_class_low[dfp$health_class < 3] <- 1
dfp$health_class_low[dfp$health_class >= 3] <- 0
dfp$health_class_upp <- NA
dfp$health_class_upp[dfp$health_class > 3] <- 1
dfp$health_class_upp[dfp$health_class <= 3] <- 0
dfp$gender_class_low <- NA
dfp$gender_class_low[dfp$gender_class < 3] <- 1
dfp$gender_class_low[dfp$gender_class >= 3] <- 0
dfp$gender_class_upp <- NA
dfp$gender_class_upp[dfp$gender_class > 3] <- 1
dfp$gender_class_upp[dfp$gender_class <= 3] <- 0
dfp_lag <- dfp <- dfp[dfp$year %in% c(seq(1965, 2015, 5), 2018), names(dfp) != "period"]
names(dfp_lag)[!names(dfp_lag) %in% c("country", "year", "period")] <- 
  paste("lag", names(dfp_lag)[!names(dfp_lag) %in% c("country", "year", "period")], sep = "_")
number_of_lags <- ifelse(params$lags %in% 1:3, params$lags, 1)
dfp_lag$year <- dfp_lag$year + 5*number_of_lags
dfp_lag$year[dfp_lag$year == 2020] <- 2018
dfp <- merge(dfp, dfp_lag, by = c("country", "year"), all.x = TRUE)
dfp <- dfp[dfp$year >= 1965 + 5*number_of_lags, ]





table(dfp$year)





dfp[, paste("growth", c(variables$health, variables$gender), sep = "_")] <- 
  lapply(c(variables$health, variables$gender), function(colname) {
    dfp[, colname] - dfp[, paste("lag", colname, sep = "_")]
  })
dfp[, paste("growth_lg", c(variables$health, "asfr_adol_wpp"), sep = "_")] <- 
  lapply(c(variables$health, "asfr_adol_wpp"), function(colname) {
    dfp[, paste("lg", colname, sep = "_")] - dfp[, paste("lag_lg", colname, sep = "_")]
  })

# functions
source("~/Dropbox/Analyses/functions/RegressionFig.R")
source("~/Dropbox/Analyses/functions/InteractionEffect.R")
RunModels <- function(equations,
  estimators_to_show = c("fe", "fegls"),
  labelspace = 18,
  pdfname = NULL,
  pdfswitch = FALSE
){
  if(is.null(names(equations))) names(equations) <- paste("m", 1:length(equations), sep = "")
  PanelModel <- function(equation, estimator, estimation_function, effect = "individual", ses = "se") {
    fit <- do.call(estimation_function, 
                   args = list(formula = equation, data = dfp, index = c("country", "year"), 
                               model = estimator, effect = effect), quote = TRUE)
    est <- data.frame(var = names(fit$coefficients), est = fit$coefficients, se = sqrt(diag(fit$vcov)))
    if(class(fit)[1] == "plm" & "crse" %in% ses & "se" %in% ses) {
      est$crse <- sqrt(diag(sandwich::vcovHC(fit, method = "arellano", type = "HC0", cluster = "group")))
    }
    if(class(fit)[1] == "plm" & !("se" %in% ses)) {
      est$se <- sqrt(diag(sandwich::vcovHC(fit, method = "arellano", type = "HC0", cluster = "group")))
    }
    info <- list(N = nrow(fit[["model"]]),
                 n = length(unique(attributes(fit$model)$index$country)),
                 T = noquote(paste(range(table(attributes(fit$model)$index$country)), collapse = "-")),
                 years = noquote(paste(range(unique(as.character(attributes(fit$model)$index$year))), 
                                       collapse = "-")))
    if(class(fit)[1] == "plm") info$rsquared = round(summary(fit)[["r.squared"]][["adjrsq"]], 2)
    if(class(fit)[1] == "pggls") info$rsquared = round(summary(fit)[["rsqr"]], 2)
    # if(class(fit)[1] == "plm") info$ftest <- summary(fit)[["fstatistic"]][["p.value"]]
    return(list(fit = fit, est = est, info = info))
  }
  estlist <- lapply(c(ols = "pooling", fe = "within", re = "random"), function(estimator) { # estimator = "within"
    lapply(equations, function(equation) { 
      PanelModel(equation = equation, estimator = estimator, estimation_function = plm::plm, ses = "crse")
    })
  })
  estlist <- c(estlist, lapply(c(ggls = "pooling", fegls = "within"), function(estimator) { # estimator = "within"
    lapply(equations, function(equation) { 
      PanelModel(equation = equation, estimator = estimator, estimation_function = plm::pggls, ses = "se")
    })
  }) )
  test_args_list <- list(
    ## unit effects
    list(testfunction = "pFtest", x_estimator = "fe", z_estimator = "ols"),
    list(testfunction = "plmtest", x_estimator = "ols"),
    list(testfunction = "plmtest", x_estimator = "ols", effect = "time"),
    list(testfunction = "plmtest", x_estimator = "ols", effect = "twoways"),
    ## correlated effects
    list(testfunction = "phtest", x_estimator = "fe", x2_estimator = "re"),
    list(testfunction = "phtest", x_estimator = "fegls", x2_estimator = "ggls", note = "(FGLS)"),
    ## any type of serial correlation of time-decaying kind in the ideosyncratic error terms
    list(testfunction = "pwtest", x_estimator = "ols"),
    ## serial correlation: detecting features of persistence
    list(testfunction = "pbsytest", x_estimator = "ols", test = "ar"),
    list(testfunction = "pbsytest", x_estimator = "ols", test = "re"),
    ## list(testfunction = "pbsytest", x_estimator = "ols", test = "j"),
    list(testfunction = "pbltest", x_estimator = "re", alternative = "onesided"),
    ## traditional serial correlation tests
    # list(testfunction = "pbgtest", x_estimator = "re", order = "2"), ## relies on large-T assymptotics
    # list(testfunction = "pdwtest", x_estimator = "re", order = "2"), ## relies on large-T assymptotics
    list(testfunction = "pwartest", x_estimator = "fe")
  )
  names(models) <- models <- unique(unlist(lapply(estlist, names)))
  results <- lapply(test_args_list, function(test_args) {
    tests <- lapply(models, function(modelname, args = test_args) {
      args$x <- estlist[[args$x_estimator]][[modelname]]$fit
      if("z_estimator" %in% names(args)) args$z <- estlist[[args$z_estimator]][[modelname]]$fit
      if("x2_estimator" %in% names(args)) args$x2 <- estlist[[args$x2_estimator]][[modelname]]$fit
      exclude <- c("testfunction", "x_estimator", "z_estimator", "note")
      test_results <- do.call(args$testfunction, args = args[!names(args) %in% exclude], quote = TRUE)
      if("note" %in% names(args)) test_results$method <- paste(test_results$method, args$note)
      data.frame(test_results[c("method", "alternative", "p.value")])
    })
    tests <- lapply(names(tests), function(modelname) {
      names(tests[[modelname]])[3] <- modelname
      return(tests[[modelname]])
    })
    Reduce(f = function(...) merge(..., by = c("method", "alternative"), all = TRUE), x = tests)
  })
  tests <- do.call(rbind, results)
  # tests$test <- paste(tests$method, " [alt. hypo.: ", tests$alternative, "]", sep = "")
  tests[, !names(tests) %in% c("method", "alternative")] <- 
    format(round(tests[, !names(tests) %in% c("method", "alternative")], 3), nsmall = 3)
  tests <- tests[, c("method", names(tests)[!names(tests) %in% c("method", "alternative")], "alternative")]
  estimators_to_show <- estimators_to_show[estimators_to_show %in% names(estlist)]
  if(pdfswitch & !is.null(pdfname)) pdf(file = paste("pdfs/", pdfname, ".pdf", sep = ""), width = 16, height = 9)
  RegressionFig(estlist = estlist[estimators_to_show], 
                labels = c(ols = "pooling models", fe = "FE models", re = "RE models", 
                           ggls = "GGLS models", fegls = "FEGLS models")[estimators_to_show], 
                labelspace = labelspace)
  if(pdfswitch & !is.null(pdfname)) dev.off()
  invisible(list(ests = estlist, tests = tests))
}
IntPlot <- function(fit, eff_var, int_vars,
  mod_vars = c(low = "lag_class_low", upp = "lag_class_upp"),
  modvalues = 1,
  title = "",
  pdfname = NULL,
  pdfswitch = FALSE
){
  confidence = 0.95
  zscore <- qnorm(1 - ((1 - confidence)/2))
  if (class(fit)[1] == "pggls") {
    varcov <- vcov(fit)
  } else {
    varcov <- sandwich::vcovHC(fit, method = "arellano", type = "HC0", cluster = "group")
  }
  ests <- lapply(int_vars, function(int_var) {
    InteractionEffect(coefs = fit$coef, varcov = varcov, effect = eff_var,  
                      moderator = mod_var[1], interaction = int_var, modvalues = 1)
  })
  ests <- do.call(rbind, lapply(ests, function(x) {
    cilower <- x$est - zscore * x$se
    ciupper <- x$est + zscore * x$se
    return(data.frame(est = x$est, cilower = cilower, ciupper = ciupper))
  }))
  ylimits <- range(list(ests, 0))
  if(pdfswitch & !is.null(pdfname)) pdf(file = paste("pdfs/", pdfname, ".pdf", sep = ""), width = 8, height = 4.5)
  plot(x = c(0.25, 0.75), y = ests$est, ylim = ylimits, xlim = c(0, 1), 
       pch = 18, ylab = "", xlab = "", xaxt = "n", main = title)
  segments(x0 = c(0.25, 0.75), y0 = ests$cilower, y1 = ests$ciupper, lwd = 2, lend = "butt")
  abline(h = 0, lwd = 0.5)
  axis(side = 1, at = c(0.25, 0.75), labels = c("low classification", "high classification"), tick = FALSE)
  if(pdfswitch & !is.null(pdfname)) dev.off()
  invisible(NULL)
}
# table(dfp[, c("class_vv")])
# dfp$lag_class_vv <- relevel(as.factor(dfp$lag_class_vv), ref = "upp")
```

## Health {.tabset .tabset-fade .tabset-pills}

### DV: Life Expectancy {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r life_exp}
results_life_exp <- RunModels(pdfname = "life_exp_wpp", equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_life_exp$tests
```

#### UCDP conflict incidence
```{r life_exp_incidence}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_life_exp$tests
```
```{r int_life_exp_incidence, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_life_exp$ests$fegls$m4$fit, 
        eff_var = "lag_conflict_one_sided", 
        int_vars = c(low = "lag_conflict_one_sided:lag_class_low", upp = "lag_conflict_one_sided:lag_class_upp"), 
        title = "Interaction Effect of One-Sided Violence on Life Expectancy", 
        pdfname = "int_life_exp_osv")
```

#### UCDP conflict incidence (NEW)
```{r life_exp_incidence_class}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_life_exp$tests
```

#### UCDP state-based conflict and OSV deaths
```{r life_exp_state_deaths}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_life_exp$tests
```
```{r int_life_exp_state_deaths, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_life_exp$ests$fegls$m4$fit, 
        eff_var = "lag_lg_deaths_civilians_int_rate", 
        int_vars = c(low = "lag_lg_deaths_civilians_int_rate:lag_class_low", 
                     # mid = "lag_lg_deaths_civilians_int_rate",
                     upp = "lag_lg_deaths_civilians_int_rate:lag_class_upp"), 
        title = "Interaction Effect of Civilian Conflict Deaths on Life Expectancy", 
        pdfname = "int_life_exp_civilians")
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r life_exp_state_deaths_class}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG +lag_lg_deaths_civilians_int_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_life_exp$tests
```

#### Societal violence deaths
```{r life_exp_nonstate_deaths}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_life_exp$tests
```

#### Societal violence deaths (NEW)
```{r life_exp_nonstate_deaths_class}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_life_exp$tests
```

#### State repression
```{r life_exp_repression}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_life_exp$tests
```
```{r int_life_exp_repression, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_life_exp$ests$fe$m2$fit, 
        eff_var = "lag_latentmean_fariss", 
        int_vars = c(low = "lag_latentmean_fariss:lag_class_low", upp = "lag_latentmean_fariss:lag_class_upp"), 
        title = "Interaction Effect of Latent Physical Integrity on Life Expectancy (FE model)", 
        pdfname = "int_life_exp_lpi_fe")
IntPlot(fit = results_life_exp$ests$fe$m4$fit, 
        eff_var = "lag_v2clkill", 
        int_vars = c(low = "lag_v2clkill:lag_class_low", upp = "lag_v2clkill:lag_class_upp"), 
        title = "Interaction Effect of Extra-Judicial Killings on Life Expectancy (FE model)", 
        pdfname = "int_life_exp_killings_fe")
IntPlot(fit = results_life_exp$ests$fegls$m4$fit, 
        eff_var = "lag_v2clkill", 
        int_vars = c(low = "lag_v2clkill:lag_class_low", upp = "lag_v2clkill:lag_class_upp"), 
        title = "Interaction Effect of Extra-Judicial Killings on Life Expectancy", 
        pdfname = "int_life_exp_killings")
```

#### State repression (NEW)
```{r life_exp_repression_class}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_life_exp$tests
```

#### Violence controls (NEW)
```{r life_exp_violence}
results_life_exp <- RunModels(equations = c(
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  life_exp_wpp ~ lag_lg_life_exp_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_life_exp$tests
```

### DV: Infant Mortality Rate (IMR) {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r imr}
results_imr <- RunModels(pdfname = "imr_wpp", equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_imr$tests
```

#### UCDP conflict incidence
```{r imr_incidence}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_imr$tests
```
```{r int_imr_incidence, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_imr$ests$fegls$m2$fit, 
        eff_var = "lag_conflict_internal", 
        int_vars = c(low = "lag_conflict_internal:lag_class_low", upp = "lag_conflict_internal:lag_class_upp"), 
        title = "Interaction Effect of Internal Conflict on Infant Mortality", 
        pdfname = "int_imr_conflict")
```

#### UCDP conflict incidence (NEW)
```{r imr_incidence_class}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_imr$tests
```

#### UCDP state-based conflict and OSV deaths
```{r imr_state_deaths}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_imr$tests
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r imr_state_deaths_class}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_imr$tests
```

#### Societal violence deaths
```{r imr_nonstate_deaths}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_imr$tests
```
```{r int_imr_deaths, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_imr$ests$fe$m6$fit, 
        eff_var = "lag_lg_hom_odcwho_rate", 
        int_vars = c(low = "lag_lg_hom_odcwho_rate:lag_class_low", upp = "lag_lg_hom_odcwho_rate:lag_class_upp"), 
        title = "Interaction Effect of Homicides on Infant Mortality (FE)", 
        pdfname = "int_imr_hom")
```

#### Societal violence deaths (NEW)
```{r imr_nonstate_deaths_class}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_imr$tests
```

#### State repression
```{r imr_repression}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_imr$tests
```
```{r int_imr_repression, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_imr$ests$fe$m2$fit, 
        eff_var = "lag_latentmean_fariss", 
        int_vars = c(low = "lag_latentmean_fariss:lag_class_low", upp = "lag_latentmean_fariss:lag_class_upp"), 
        title = "Interaction Effect of Latent Physical Integrity on Infant Mortality (FE)", 
        pdfname = "int_imr_lpi_fe")
IntPlot(fit = results_imr$ests$fegls$m2$fit, 
        eff_var = "lag_latentmean_fariss", 
        int_vars = c(low = "lag_latentmean_fariss:lag_class_low", upp = "lag_latentmean_fariss:lag_class_upp"), 
        title = "Interaction Effect of Latent Physical Integrity on Infant Mortality", 
        pdfname = "int_imr_lpi")
IntPlot(fit = results_imr$ests$fe$m4$fit, 
        eff_var = "lag_v2clkill", 
        int_vars = c(low = "lag_v2clkill:lag_class_low", upp = "lag_v2clkill:lag_class_upp"), 
        title = "Interaction Effect of Extra-Judicial Killings on Infant Mortality (FE)", 
        pdfname = "int_imr_killings_fe")
IntPlot(fit = results_imr$ests$fegls$m4$fit, 
        eff_var = "lag_v2clkill", 
        int_vars = c(low = "lag_v2clkill:lag_class_low", upp = "lag_v2clkill:lag_class_upp"), 
        title = "Interaction Effect of Extra-Judicial Killings on Infant Mortality", 
        pdfname = "int_imr_killings")
IntPlot(fit = results_imr$ests$fe$m6$fit, 
        eff_var = "lag_v2cltort", 
        int_vars = c(low = "lag_v2cltort:lag_class_low", upp = "lag_v2cltort:lag_class_upp"), 
        title = "Interaction Effect of State Torture on Infant Mortality (FE)", 
        pdfname = "int_imr_torture_fe")
IntPlot(fit = results_imr$ests$fegls$m6$fit, 
        eff_var = "lag_v2cltort", 
        int_vars = c(low = "lag_v2cltort:lag_class_low", upp = "lag_v2cltort:lag_class_upp"), 
        title = "Interaction Effect of State Torture on Infant Mortality", 
        pdfname = "int_imr_torture")
```

#### State repression (NEW)
```{r imr_repression_class}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_imr$tests
```

#### Violence controls (NEW)
```{r imr_violence}
results_imr <- RunModels(equations = c(
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  imr_wpp ~ lag_lg_imr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_imr$tests
```

### NEW DV: Under-five Mortality Rate (UFMR) {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r ufmr}
results_ufmr <- RunModels(pdfname = "ufmr_wpp", equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_ufmr$tests
```

#### UCDP conflict incidence
```{r ufmr_incidence}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_ufmr$tests
```

#### UCDP conflict incidence (NEW)
```{r ufmr_incidence_class}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_ufmr$tests
```

#### UCDP state-based conflict and OSV deaths
```{r ufmr_state_deaths}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_ufmr$tests
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r ufmr_state_deaths_class}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_ufmr$tests
```

#### Societal violence deaths
```{r ufmr_nonstate_deaths}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_ufmr$tests
```

#### Societal violence deaths (NEW)
```{r ufmr_nonstate_deaths_class}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_ufmr$tests
```

#### State repression
```{r ufmr_repression}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_ufmr$tests
```

#### State repression (NEW)
```{r ufmr_repression_class}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_ufmr$tests
```

#### Violence controls (NEW)
```{r ufmr_violence}
results_ufmr <- RunModels(equations = c(
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  ufmr_wpp ~ lag_lg_ufmr_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_ufmr$tests
```

### NEW DV: Disability-adjusted life years (DALYs) {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r daly}
results_daly <- RunModels(pdfname = "daly_ihme", equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_daly$tests
```

#### UCDP conflict incidence
```{r daly_incidence}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_daly$tests
```

#### UCDP conflict incidence (NEW)
```{r daly_incidence_class}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_daly$tests
```

#### UCDP state-based conflict and OSV deaths
```{r daly_state_deaths}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_daly$tests
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r daly_state_deaths_class}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_daly$tests
```

#### Societal violence deaths
```{r daly_nonstate_deaths}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_daly$tests
```

#### Societal violence deaths (NEW)
```{r daly_nonstate_deaths_class}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_daly$tests
```

#### State repression
```{r daly_repression}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_daly$tests
```

#### State repression (NEW)
```{r daly_repression_class}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_daly$tests
```

#### Violence controls (NEW)
```{r daly_violence}
results_daly <- RunModels(equations = c(
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  daly_ihme ~ lag_lg_daly_ihme + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_daly$tests
```

## Gender {.tabset .tabset-fade .tabset-pills}

### DV: Mean Years of School, ratio of female to male {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r mys}
results_mys_ratio <- RunModels(pdfname = "mys_ratio_hdr", equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_mys_ratio$tests
```

#### UCDP conflict incidence
```{r mys_incidence}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_mys_ratio$tests
```
```{r int_mys_incidence, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_mys_ratio$ests$fegls$m4$fit, 
        eff_var = "lag_conflict_one_sided", 
        int_vars = c(low = "lag_conflict_one_sided:lag_class_low", 
                     upp = "lag_conflict_one_sided:lag_class_upp"), 
        title = "Interaction Effect of One-Sided Violence on Mean Years of Schooling", 
        pdfname = "int_mys_osv")
```

#### UCDP conflict incidence (NEW)
```{r mys_incidence_class}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_mys_ratio$tests
```

#### UCDP state-based conflict and OSV deaths
```{r mys_state_deaths}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp
))
results_mys_ratio$tests
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r mys_state_deaths_class}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp
))
results_mys_ratio$tests
```

#### Societal violence deaths
```{r mys_nonstate_deaths}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_mys_ratio$tests
```
```{r int_mys_deaths, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_mys_ratio$ests$fe$m4$fit, 
        eff_var = "lag_lg_deaths_civilians_nsc_rate", 
        int_vars = c(low = "lag_lg_deaths_civilians_nsc_rate:lag_class_low", 
                     upp = "lag_lg_deaths_civilians_nsc_rate:lag_class_upp"), 
        title = "Interaction Effect of Non-State Conflict Civilian Deaths\non Mean Years of Schooling", 
        pdfname = "int_mys_lpi")
```

#### Societal violence deaths (NEW)
```{r mys_nonstate_deaths_class}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  # mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_mys_ratio$tests
```

#### State repression
```{r mys_repression}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_mys_ratio$tests
```
```{r int_mys_repression, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_mys_ratio$ests$fegls$m2$fit, 
        eff_var = "lag_latentmean_fariss", 
        int_vars = c(low = "lag_latentmean_fariss:lag_class_low", upp = "lag_latentmean_fariss:lag_class_upp"), 
        title = "Interaction Effect of Latent Physical Integrity on Mean Years of Schooling", 
        pdfname = "int_mys_lpi")
IntPlot(fit = results_mys_ratio$ests$fe$m4$fit, 
        eff_var = "lag_v2clkill", 
        int_vars = c(low = "lag_v2clkill:lag_class_low", upp = "lag_v2clkill:lag_class_upp"), 
        title = "Interaction Effect of Extra-judicial killings on Mean Years of Schooling", 
        pdfname = "int_mys_killings_fe")
IntPlot(fit = results_mys_ratio$ests$fe$m6$fit, 
        eff_var = "lag_v2cltort", 
        int_vars = c(low = "lag_v2cltort:lag_class_low", upp = "lag_v2cltort:lag_class_upp"), 
        title = "Interaction Effect of State Torture on Mean Years of Schooling", 
        pdfname = "int_mys_torture_fe")
```

#### State repression (NEW)
```{r mys_repression_class}
results_mys_ratio <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_mys_ratio$tests
```

#### Violence controls (NEW)
```{r mys_violence}
results_mys <- RunModels(equations = c(
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  mys_ratio_hdr ~ lag_mys_ratio_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_mys$tests
```

### DV: Adolescent Fertility Rate {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r asfr}
results_asfr <- RunModels(pdfname = "asfr_adol_wpp", equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_asfr$tests
```

#### UCDP conflict incidence
```{r asfr_incidence}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_asfr$tests
```
```{r int_asfr_incidence, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_asfr$ests$fe$m2$fit, 
        eff_var = "lag_conflict_internal", 
        int_vars = c(low = "lag_conflict_internal:lag_class_low", upp = "lag_conflict_internal:lag_class_upp"), 
        title = "Interaction Effect of Internal Conflict on Adolescent Fertility Rate", 
        pdfname = "int_asfr_conflict_fe")
IntPlot(fit = results_asfr$ests$fegls$m4$fit, 
        eff_var = "lag_conflict_one_sided", 
        int_vars = c(low = "lag_conflict_one_sided:lag_class_low", upp = "lag_conflict_one_sided:lag_class_upp"), 
        title = "Interaction Effect of One-Sided Violence on Adolescent Fertility Rate", 
        pdfname = "int_asfr_osv")
```

#### UCDP conflict incidence (NEW)
```{r asfr_incidence_class}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_asfr$tests
```

#### UCDP state-based conflict and OSV deaths
```{r asfr_state_deaths}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_asfr$tests
```
```{r int_asfr_state_deaths, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_asfr$ests$fegls$m2$fit, 
        eff_var = "lag_lg_deaths_all_int_rate", 
        int_vars = c(low = "lag_lg_deaths_all_int_rate:lag_class_low", 
                     upp = "lag_lg_deaths_all_int_rate:lag_class_upp"), 
        title = "Interaction Effect of Conflict Deaths on Adolescent Fertility Rate", 
        pdfname = "int_asfr_deaths")
IntPlot(fit = results_asfr$ests$fegls$m4$fit, 
        eff_var = "lag_lg_deaths_civilians_int_rate", 
        int_vars = c(low = "lag_lg_deaths_civilians_int_rate:lag_class_low", 
                     upp = "lag_lg_deaths_civilians_int_rate:lag_class_upp"), 
        title = "Interaction Effect of Civilian Conflict Deaths on Adolescent Fertility Rate", 
        pdfname = "int_asfr_cvilians")
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r asfr_state_deaths_class}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_asfr$tests
```

#### Societal violence deaths
```{r asfr_nonstate_deaths}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_asfr$tests
```

#### Societal violence deaths (NEW)
```{r asfr_nonstate_deaths_class}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_asfr$tests
```

#### State repression
```{r asfr_repression}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_asfr$tests
```
```{r int_asfr_repression, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_asfr$ests$fegls$m6$fit, 
        eff_var = "lag_v2cltort", 
        int_vars = c(low = "lag_v2cltort:lag_class_low", upp = "lag_v2cltort:lag_class_upp"), 
        title = "Interaction Effect of State Torture on Adolescent Fertility Rate", 
        pdfname = "int_asfr_torture")
```

#### State repression (NEW)
```{r asfr_repression_class}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_asfr$tests
```

#### Violence controls (NEW)
```{r asfr_violence}
results_asfr <- RunModels(equations = c(
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  asfr_adol_wpp ~ lag_lg_asfr_adol_wpp + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_asfr$tests
```

### NEW DV: Labour participation ratio {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r labor}
results_labor <- RunModels(pdfname = "labor_mod_ratio15_ilo", equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_labor$tests
```

#### UCDP conflict incidence
```{r labor_incidence}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_labor$tests
```

#### UCDP conflict incidence (NEW)
```{r labor_incidence_class}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_labor$tests
```

#### UCDP state-based conflict and OSV deaths
```{r labor_state_deaths}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_labor$tests
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r labor_state_deaths_class}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_labor$tests
```

#### Societal violence deaths
```{r labor_nonstate_deaths}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_labor$tests
```

#### Societal violence deaths (NEW)
```{r labor_nonstate_deaths_class}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_labor$tests
```

#### State repression
```{r labor_repression}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_labor$tests
```

#### State repression (NEW)
```{r labor_repression_class}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_labor$tests
```

#### Violence controls (NEW)
```{r labor_violence}
results_labor <- RunModels(equations = c(
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  labor_mod_ratio15_ilo ~ lag_labor_mod_ratio15_ilo + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_labor$tests
```

### NEW DV: Gender inequality index (GII) {.tabset .tabset-fade .tabset-pills}

#### Base models
```{r gii}
results_gii <- RunModels(pdfname = "gii_hdr", equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp)
)
results_gii$tests
```

#### UCDP conflict incidence
```{r gii_incidence}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_internal,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_one_sided,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_conflict_non_state,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_gii$tests
```

#### UCDP conflict incidence (NEW)
```{r gii_incidence_class}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_internal,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_one_sided,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_conflict_non_state,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_upp)
)
results_gii$tests
```

#### UCDP state-based conflict and OSV deaths
```{r gii_state_deaths}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_int_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_gii$tests
```

#### UCDP state-based conflict and OSV deaths (NEW)
```{r gii_state_deaths_class}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_int_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_int_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_osv_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_gii$tests
```

#### Societal violence deaths
```{r gii_nonstate_deaths}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_lg_hom_odcwho_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_gii$tests
```

#### Societal violence deaths (NEW)
```{r gii_nonstate_deaths_class}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_all_nsc_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_deaths_civilians_nsc_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_lg_hom_odcwho_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_gii$tests
```

#### State repression
```{r gii_repression}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_latentmean_fariss,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2clkill,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp + lag_v2cltort,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_gii$tests
```

#### State repression (NEW)
```{r gii_repression_class}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_latentmean_fariss,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2clkill,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_upp,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_mid + lag_class_GH + lag_class_HG + lag_class_upp + lag_v2cltort,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_upp)
)
results_gii$tests
```

#### Violence controls (NEW)
```{r gii_violence}
results_gii <- RunModels(equations = c(
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate,
  gii_hdr ~ lag_gii_hdr + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_gii$tests
```

## Violence {.tabset .tabset-fade .tabset-pills}

### Correlations

```{r violence, message = FALSE, warning = FALSE, results = 'hide'}
vars_viol <- c("conflict_internal", "conflict_one_sided", "conflict_non_state", "lg_deaths_all_int_rate", "lg_deaths_civilians_osv_rate", "lg_deaths_all_nsc_rate", "lg_hom_odcwho_rate", "latentmean_fariss", "v2clkill")
GGally::ggpairs(dfp[, vars_viol], mapping = aes(stroke = 0, alpha = 0.25)) + 
  theme_bw() + 
  theme(strip.text.y.right = element_text(angle = 0)) + 
  ggtitle("Different types of violence")
```

### DV: Internal Conflict
```{r conflict}
results_conflict <- RunModels(pdfname = "viol_conflict_internal", labelspace = 20, equations = c(
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  conflict_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_upp)
) 
results_conflict$tests
```

### DV: Internal Conflict (NEW)
```{r conflict_class}
results_conflict <- RunModels(pdfname = "viol_conflict_internal", labelspace = 20, equations = c(
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  conflict_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_mid,
  conflict_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_low + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_upp,
  conflict_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_internal*lag_class_HG + lag_conflict_internal*lag_class_GH + lag_conflict_internal*lag_class_mid + lag_conflict_internal*lag_class_upp,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  conflict_internal ~ lag_conflict_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
) 
results_conflict$tests
```

### DV: Internal War
```{r war}
results_war <- RunModels(pdfname = "viol_war_internal", labelspace = 20, equations = c(
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  war_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_war_internal*lag_class_low + lag_war_internal*lag_class_upp)
)
results_war$tests
```
```{r int_war, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_war$ests$fegls$m6$fit, 
        eff_var = "lag_war_internal", 
        int_vars = c(low = "lag_war_internal:lag_class_low", upp = "lag_war_internal:lag_class_upp"), 
        title = "Interaction Effect of lagged Internal War", 
        pdfname = "int_war")
```

### DV: Internal War (NEW)
```{r war_class}
results_war <- RunModels(pdfname = "viol_war_internal", labelspace = 20, equations = c(
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  war_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_war_internal*lag_class_low + lag_war_internal*lag_class_HG + lag_war_internal*lag_class_GH + lag_war_internal*lag_class_mid,
  war_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_war_internal*lag_class_low + lag_war_internal*lag_class_HG + lag_war_internal*lag_class_GH + lag_war_internal*lag_class_upp,
  war_internal ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_war_internal*lag_class_HG + lag_war_internal*lag_class_GH + lag_war_internal*lag_class_mid + lag_war_internal*lag_class_upp,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  war_internal ~ lag_war_internal + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_war$tests
```

### DV: Internal Conflict Deaths
```{r conflict_deaths}
results_intd <- RunModels(pdfname = "viol_deaths_all_int_rate", labelspace = 20, equations = c(
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  deaths_all_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_upp)
)
results_intd$tests
```
```{r int_conflict_deaths, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_intd$ests$fegls$m6$fit, 
        eff_var = "lag_lg_deaths_all_int_rate", 
        int_vars = c(low = "lag_lg_deaths_all_int_rate:lag_class_low", 
                     upp = "lag_lg_deaths_all_int_rate:lag_class_upp"), 
        title = "Interaction Effect of lagged Conflict Deaths", 
        pdfname = "int_conflict_deaths")
```

### DV: Internal Conflict Deaths (NEW)
```{r conflict_deaths_class}
results_intd <- RunModels(pdfname = "viol_deaths_all_int_rate", labelspace = 20, equations = c(
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  deaths_all_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_mid,
  deaths_all_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_low + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_upp,
  deaths_all_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_int_rate*lag_class_HG + lag_lg_deaths_all_int_rate*lag_class_GH + lag_lg_deaths_all_int_rate*lag_class_mid + lag_lg_deaths_all_int_rate*lag_class_upp,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  deaths_all_int_rate ~ lag_lg_deaths_all_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_intd$tests
```

### DV: Internal Conflict Civilian Deaths
```{r conflict_deaths_civ}
results_civ <- RunModels(pdfname = "viol_deaths_civilians_int_rate", labelspace = 20, equations = c(
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  deaths_civilians_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_upp)
)
results_civ$tests
```
```{r int_conflict_deaths_civ, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_civ$ests$fe$m6$fit, 
        eff_var = "lag_lg_deaths_civilians_int_rate", 
        int_vars = c(low = "lag_lg_deaths_civilians_int_rate:lag_class_low", 
                     upp = "lag_lg_deaths_civilians_int_rate:lag_class_upp"), 
        title = "Interaction Effect of lagged Civilian Conflict Deaths (FE model)", 
        pdfname = "int_deaths_civ_fe")
IntPlot(fit = results_civ$ests$fegls$m6$fit, 
        eff_var = "lag_lg_deaths_civilians_int_rate", 
        int_vars = c(low = "lag_lg_deaths_civilians_int_rate:lag_class_low", 
                     upp = "lag_lg_deaths_civilians_int_rate:lag_class_upp"), 
        title = "Interaction Effect of lagged Civilian Conflict Deaths (FEGLS model)", 
        pdfname = "int_deaths_civ_fegls")
```

### DV: Internal Conflict Civilian Deaths (NEW)
```{r conflict_deaths_civ_class}
results_civ <- RunModels(pdfname = "viol_deaths_civilians_int_rate", labelspace = 20, equations = c(
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  deaths_civilians_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_mid,
  deaths_civilians_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_low + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  deaths_civilians_int_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_int_rate*lag_class_HG + lag_lg_deaths_civilians_int_rate*lag_class_GH + lag_lg_deaths_civilians_int_rate*lag_class_mid + lag_lg_deaths_civilians_int_rate*lag_class_upp,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_civ$tests
```

### DV: One-Sided Violence
```{r osv}
results_osv <- RunModels(labelspace = 20, equations = c(
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  conflict_one_sided ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_upp)
)
results_osv$tests
```

### DV: One-Sided Violence (NEW)
```{r osv_class}
results_osv <- RunModels(labelspace = 20, equations = c(
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  conflict_one_sided ~ lag_conflict_one_sided + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  conflict_one_sided ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_mid,
  conflict_one_sided ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_low + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_upp,
  conflict_one_sided ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_one_sided*lag_class_HG + lag_conflict_one_sided*lag_class_GH + lag_conflict_one_sided*lag_class_mid + lag_conflict_one_sided*lag_class_upp,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  deaths_civilians_int_rate ~ lag_lg_deaths_civilians_int_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_osv$tests
```

### DV: OSV Civilian Deaths
```{r osv_deaths}
results_osvd <- RunModels(pdfname = "viol_deaths_civilians_osv_rate", labelspace = 20, equations = c(
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  deaths_civilians_osv_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_upp)
)
results_osvd$tests
```

### DV: OSV Civilian Deaths (NEW)
```{r osv_deaths_class}
results_osvd <- RunModels(pdfname = "viol_deaths_civilians_osv_rate", labelspace = 20, equations = c(
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  deaths_civilians_osv_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_mid,
  deaths_civilians_osv_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_low + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_upp,
  deaths_civilians_osv_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_osv_rate*lag_class_HG + lag_lg_deaths_civilians_osv_rate*lag_class_GH + lag_lg_deaths_civilians_osv_rate*lag_class_mid + lag_lg_deaths_civilians_osv_rate*lag_class_upp,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  deaths_civilians_osv_rate ~ lag_lg_deaths_civilians_osv_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_osvd$tests
```

### DV: Non-State Conflict

```{r nsc}
results_nsc <- RunModels(pdfname = "viol_conflict_non_state", labelspace = 20, equations = c(
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  conflict_non_state ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_upp)
)
results_nsc$tests
```

### DV: Non-State Conflict (NEW)

```{r nsc_class}
results_nsc <- RunModels(pdfname = "viol_conflict_non_state", labelspace = 20, equations = c(
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  conflict_non_state ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_mid,
  conflict_non_state ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_low + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_upp,
  conflict_non_state ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_conflict_non_state*lag_class_HG + lag_conflict_non_state*lag_class_GH + lag_conflict_non_state*lag_class_mid + lag_conflict_non_state*lag_class_upp,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_latentmean_fariss,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  conflict_non_state ~ lag_conflict_non_state + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_nsc$tests
```

### DV: NSC Deaths
```{r nsc_deaths}
results_nscd <- RunModels(pdfname = "viol_deaths_all_nsc_rate", labelspace = 20, equations = c(
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  deaths_all_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_upp)
)
results_nscd$tests
```
```{r int_nsc_deaths, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_nscd$ests$fe$m6$fit, 
        eff_var = "lag_lg_deaths_all_nsc_rate", 
        int_vars = c(low = "lag_lg_deaths_all_nsc_rate:lag_class_low", 
                     upp = "lag_lg_deaths_all_nsc_rate:lag_class_upp"), 
        title = "Interaction Effect of lagged NSC Deaths (FE model)", 
        pdfname = "int_nsc_deaths_fe")
IntPlot(fit = results_nscd$ests$fegls$m6$fit, 
        eff_var = "lag_lg_deaths_all_nsc_rate", 
        int_vars = c(low = "lag_lg_deaths_all_nsc_rate:lag_class_low", 
                     upp = "lag_lg_deaths_all_nsc_rate:lag_class_upp"), 
        title = "Interaction Effect of lagged NSC Deaths (FEGLS model)", 
        pdfname = "int_nsc_deaths_fegls")
```

### DV: NSC Deaths (NEW)
```{r nsc_deaths_class}
results_nscd <- RunModels(pdfname = "viol_deaths_all_nsc_rate", labelspace = 20, equations = c(
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  deaths_all_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_mid,
  deaths_all_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_low + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  deaths_all_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_all_nsc_rate*lag_class_HG + lag_lg_deaths_all_nsc_rate*lag_class_GH + lag_lg_deaths_all_nsc_rate*lag_class_mid + lag_lg_deaths_all_nsc_rate*lag_class_upp,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_latentmean_fariss,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  deaths_all_nsc_rate ~ lag_lg_deaths_all_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_nscd$tests
```

### DV: NSC Civilian Deaths
```{r nsc_deaths_civ}
results_nscd_civ <- RunModels(pdfname = "viol_deaths_civilians_nsc_rate", labelspace = 20, equations = c(
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  deaths_civilians_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_upp)
)
results_nscd_civ$tests
```

### DV: NSC Civilian Deaths (NEW)
```{r nsc_deaths_civ_class}
results_nscd_civ <- RunModels(pdfname = "viol_deaths_civilians_nsc_rate", labelspace = 20, equations = c(
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  deaths_civilians_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_mid,
  deaths_civilians_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_low + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  deaths_civilians_nsc_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_deaths_civilians_nsc_rate*lag_class_HG + lag_lg_deaths_civilians_nsc_rate*lag_class_GH + lag_lg_deaths_civilians_nsc_rate*lag_class_mid + lag_lg_deaths_civilians_nsc_rate*lag_class_upp,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_latentmean_fariss,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss,
  deaths_civilians_nsc_rate ~ lag_lg_deaths_civilians_nsc_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss + lag_lg_hom_odcwho_rate)
)
results_nscd_civ$tests
```

### DV: Latent Physical Integrity
```{r lpi}
results_lpi <- RunModels(pdfname = "viol_latentmean_fariss", labelspace = 20, equations = c(
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  latentmean_fariss ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_upp)
)
results_lpi$tests
```
```{r int_lpi, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_lpi$ests$fegls$m6$fit, 
        eff_var = "lag_latentmean_fariss", 
        int_vars = c(low = "lag_latentmean_fariss:lag_class_low", upp = "lag_latentmean_fariss:lag_class_upp"), 
        title = "Interaction Effect of lagged Latent Physical Integrity", 
        pdfname = "int_lpi")
```

### DV: Latent Physical Integrity (NEW)
```{r lpi_class}
results_lpi <- RunModels(pdfname = "viol_latentmean_fariss", labelspace = 20, equations = c(
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  latentmean_fariss ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_mid,
  latentmean_fariss ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_low + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_upp,
  latentmean_fariss ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_latentmean_fariss*lag_class_HG + lag_latentmean_fariss*lag_class_GH + lag_latentmean_fariss*lag_class_mid + lag_latentmean_fariss*lag_class_upp,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  latentmean_fariss ~ lag_latentmean_fariss + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_lg_hom_odcwho_rate)
)
results_lpi$tests
```

### DV: Torture
```{r torture}
results_tort <- RunModels(labelspace = 20, equations = c(
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  v2cltort ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_upp)
)
results_tort$tests
```

### DV: Torture (NEW)
```{r torture_class}
results_tort <- RunModels(labelspace = 20, equations = c(
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  v2cltort ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_mid,
  v2cltort ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_low + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_upp,
  v2cltort ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2cltort*lag_class_HG + lag_v2cltort*lag_class_GH + lag_v2cltort*lag_class_mid + lag_v2cltort*lag_class_upp,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  v2cltort ~ lag_v2cltort + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_lg_hom_odcwho_rate)
)
results_tort$tests
```

### DV: Extra-Judicial Killings
```{r killings}
results_kill <- RunModels(pdfname = "viol_v2clkill", labelspace = 20, equations = c(
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  v2clkill ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_upp)
)
results_kill$tests
```
```{r int_killings, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_kill$ests$fegls$m6$fit, 
        eff_var = "lag_v2clkill", 
        int_vars = c(low = "lag_v2clkill:lag_class_low", upp = "lag_v2clkill:lag_class_upp"), 
        title = "Interaction Effect of lagged Extra-Judicial Killings", 
        pdfname = "int_killings")
```

### DV: Extra-Judicial Killings (NEW)
```{r killings_class}
results_kill <- RunModels(pdfname = "viol_v2clkill", labelspace = 20, equations = c(
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  v2clkill ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_mid,
  v2clkill ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_low + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_upp,
  v2clkill ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_v2clkill*lag_class_HG + lag_v2clkill*lag_class_GH + lag_v2clkill*lag_class_mid + lag_v2clkill*lag_class_upp,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  v2clkill ~ lag_v2clkill + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_lg_hom_odcwho_rate)
)
results_kill$tests
```

### DV: Homicides
```{r homicides}
results_hom <- RunModels(pdfname = "viol_hom_odcwho_rate", labelspace = 20, equations = c(
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_life_exp_wpp,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_imr_wpp,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_mys_ratio_hdr,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_asfr_adol_wpp,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_upp,
  hom_odcwho_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_upp)
)
results_hom$tests
```
```{r int_homicides, fig.width = 7, fig.height = 5, out.width = "33%", out.height = "33%", fig.show = 'hold'}
IntPlot(fit = results_hom$ests$fe$m6$fit, 
        eff_var = "lag_lg_hom_odcwho_rate", 
        int_vars = c(low = "lag_lg_hom_odcwho_rate:lag_class_low", 
                     upp = "lag_lg_hom_odcwho_rate:lag_class_upp"), 
        title = "Interaction Effect of lagged Homicides (FE model)", 
        pdfname = "int_homicides_fe")
IntPlot(fit = results_hom$ests$fegls$m6$fit, 
        eff_var = "lag_lg_hom_odcwho_rate", 
        int_vars = c(low = "lag_lg_hom_odcwho_rate:lag_class_low", 
                     upp = "lag_lg_hom_odcwho_rate:lag_class_upp"), 
        title = "Interaction Effect of lagged Homicides (FEGLS model)", 
        pdfname = "int_homicides_fegls")
```

### DV: Homicides (NEW)
```{r homicides_class}
results_hom <- RunModels(pdfname = "viol_hom_odcwho_rate", labelspace = 20, equations = c(
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_mid,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_low + lag_class_HG + lag_class_GH + lag_class_upp,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp,
  hom_odcwho_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_mid,
  hom_odcwho_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_low + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_upp,
  hom_odcwho_rate ~ lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_lg_hom_odcwho_rate*lag_class_HG + lag_lg_hom_odcwho_rate*lag_class_GH + lag_lg_hom_odcwho_rate*lag_class_mid + lag_lg_hom_odcwho_rate*lag_class_upp,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_latentmean_fariss,
  hom_odcwho_rate ~ lag_lg_hom_odcwho_rate + lag_lg_pc_rgdpe_pwt + lag_lg_pop_wpp + lag_v2x_partipdem + lag_class_HG + lag_class_GH + lag_class_mid + lag_class_upp + lag_lg_deaths_civilians_int_rate + lag_lg_deaths_civilians_nsc_rate + lag_lg_deaths_civilians_osv_rate + lag_latentmean_fariss)
)
results_hom$tests
```

```{r stationarity, echo = FALSE, eval = FALSE, include = FALSE}
# new <- na.omit(data[data$year %in% seq(1970, 2015, 5), c("country", "year", "pc_rgdpe_pwt")])
# new <- make.pbalanced(new, balance.type = "shared.individuals", index = c("country", "year"))
# purtest(pc_rgdpe_pwt ~1, data = new, index = c("country", "year"), test = "levinlin", lags = "AIC", pmax = 2)
# table(data$year, is.na(data$life_exp_wpp))
```
