---
title: "Mapping trajectories"
params: 
  cache: false
  optimize: true
---

```{r setup, include = FALSE}
source("setup.R")
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      fig.show = "hold",
                      fig.width = 5, fig.height = 5, 
                      out.width = "50%", out.height = "50%",
                      rownames.print = FALSE, rows.print = 12, 
                      cols.print = 10, cols.min.print = 10)
```
### {.tabset .tabset-fade .tabset-pills}

```{r data, results = "hide"}
IsTrue <- function(x) { !is.na(x) & x }
load("_data/LSCMWG_working_class.RData")
link <- "https://docs.google.com/spreadsheets/d/1KPUMNCixfyFU4KryzV0_5BYUHCUIyOq2heei9KdpSF8/edit?usp=sharing"
googlesheets4::gs4_deauth()
seq <- googlesheets4::read_sheet(link, sheet = "coding", na = "..")
save(seq, file = "_data/sequences.RData")
```

```{r class, results = 'hide', out.width = "25%", out.height = "25%", eval = FALSE, echo = FALSE}
df <- unique(df[, c("country", "period", "health_class", "gender_class", "class", "class_vv")])
df$period <- str_sub(df$period, 7, 10)
df <- df[!is.na(df$class) & df$period != 2020, ]
df_new <- pivot_wider(df[, c("country", "period", "class_vv")], names_from = period, values_from = class_vv)
df_new[, -1] <- lapply(df_new[, -1], function(col) {
  col[is.na(col)] <- ""
  return(col)
})
as.data.frame(df_new)
df_new <- pivot_wider(df[, c("country", "period", "class")], names_from = period, values_from = class)
df_new[, -1] <- lapply(df_new[, -1], function(col) {
  col[is.na(col)] <- ""
  return(col)
})
df <- df %>% arrange(country, period)
df <- df %>% group_by(country) %>% 
  mutate(lag_health_class = lag(health_class), lag_gender_class = lag(gender_class), lag_class = lag(class))
df <- df[!is.na(df$lag_class), ]
df <- df[IsTrue(df$lag_class != df$class), ]
list(as.data.frame(df_new[df_new$country %in% df_new$country[!df_new$country %in% unique(df$country)], ]))
lapply(unique(df$country), function(ctry) {
  ggplot(df[df$country == ctry, ], 
         aes(x = lag_gender_class, y = lag_health_class, xend = gender_class, yend = health_class)) + 
    geom_segment(arrow = arrow(angle = 15, type = "closed")) + 
    geom_point(aes(x = lag_gender_class[period == min(period)], 
                   y = lag_health_class[period == min(period)]), 
               shape = 22, size = 3, fill = "red") + 
    geom_point(aes(x = gender_class[period == max(period)], 
                   y = health_class[period == max(period)]), 
               shape = 23, size = 3, fill = "green") + 
    coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 5.5)) + 
    labs(x = "Gender", y = "Health") + theme_classic() + ggtitle(ctry)
})
```

```{r sequencing, results = 'hide', out.width = "25%", out.height = "25%"}
missing_countries <- c("Andorra", "Czechoslovakia", "Dominica", "East Germany", "Ethiopia", "Kosovo", "Liechtenstein", "Marshall Islands", "Monaco", "Nauru", "North Vietnam", "North Yemen", "Palau", "San Marino", "Saint Kitts & Nevis", "South Vietnam", "South Yemen", "Soviet Union", "Tuvalu", "West Germany", "Yugoslavia SFR", "South Sudan", "Serbia & Montenegro")
# table(df[, c("conf_intra", "wars_intra")])
ViolenceCats <- function(dataset = df[!(df$country %in% missing_countries), ], start_yr = 1975, end_yr = 2015, yrs_long = 3) {
  df <- dataset %>% select(country, year, conf_intra, wars_intra, latentmean_fariss, v2caviol, v2clkill, v2cltort) %>%
    filter(year >= start_yr & year <= end_yr) %>%
    arrange(country, year) %>%
    group_by(country) %>%
    mutate(conflict_yrs = sum(conf_intra > 0),
           war_yrs = sum(wars_intra > 0),
           latentmean_fariss = mean(latentmean_fariss, na.rm = TRUE),
           v2caviol = mean(v2caviol, na.rm = TRUE),
           v2clkill = mean(v2clkill, na.rm = TRUE),
           v2cltort = mean(v2cltort, na.rm = TRUE)) %>%
    filter(year == end_yr)
  df$conflict[df$conflict_yrs > 0] <- "conflict"
  df$conflict[df$conflict_yrs > (yrs_long -1)] <- paste("conflict (", yrs_long, "+ yrs)", sep = "")
  df$conflict[df$war_yrs > 0] <- "war"
  df$conflict[df$war_yrs > (yrs_long -1)] <- paste("war (", yrs_long, "+ yrs)", sep = "")
  df$conflict[df$conflict_yrs == 0 & df$war_yrs == 0] <- "none"
  df$conflict <- as.factor(df$conflict)
  df <- df %>% select(country, latentmean_fariss, v2caviol, v2clkill, v2cltort, conflict)
  vars <- c("latentmean_fariss", "v2caviol", "v2clkill", "v2cltort")
  df[, vars] <- lapply(df[, vars], function(col) {
    col[is.nan(col)] <- NA
    col
    # new <- rep(NA, length(col))
    # new[col >= quantile(col, na.rm = TRUE)[1]] <- "1st quartile"
    # new[col >= quantile(col, na.rm = TRUE)[2]] <- "2nd quartile"
    # new[col >= quantile(col, na.rm = TRUE)[3]] <- "3rd quartile"
    # new[col >= quantile(col, na.rm = TRUE)[4]] <- "4th quartile"
    # return(as.factor(new))
  })
  names(df)[-1] <- paste(names(df)[-1], start_yr, end_yr, sep = "_")
  return(df)
}
# 1961-1970 < seq starts 1975 (1971-1975) <= 1971-2015
# 1981-1990 < seq starts 1995 (1991-1995) <= 1991-2015
violence <- list(
  ViolenceCats(start_yr = 1971, end_yr = 2015, yrs_long = 5),
  ViolenceCats(start_yr = 1971, end_yr = 1995, yrs_long = 5),
  ViolenceCats(start_yr = 1976, end_yr = 1995, yrs_long = 5),
  ViolenceCats(start_yr = 1976, end_yr = 2015, yrs_long = 5),
  ViolenceCats(start_yr = 1991, end_yr = 2015, yrs_long = 5),
  ViolenceCats(start_yr = 1996, end_yr = 2015, yrs_long = 5)
)
violence <- Reduce(f = function(...) merge(..., by = "country", all = TRUE), x = violence)
# vars <- names(df)
# vars <- vars[!str_detect(vars, "perf_")]
# lapply(c(variables$health, variables$gender), function(x) {
#   vars[str_detect(vars, x)]
# })
# vars[str_detect(vars, "class") ]
df <- df[df$year > 1970, ] %>% 
  arrange(country, year) %>% 
  group_by(country, period) %>% 
  mutate(latentmean_fariss_avg = mean(latentmean_fariss, na.rm = TRUE),
         v2caviol_avg = mean(v2caviol, na.rm = TRUE),
         v2clkill_avg = mean(v2clkill, na.rm = TRUE),
         v2cltort_avg = mean(v2cltort, na.rm = TRUE),
         hom_odcwho_rate_avg = mean(hom_odcwho_rate, na.rm = TRUE),
         deaths_all_int_rate_avg = mean(deaths_all_int_rate, na.rm = TRUE),
         deaths_all_nsc_rate_avg = mean(deaths_all_nsc_rate, na.rm = TRUE),
         deaths_civilians_osv_rate_avg = mean(deaths_civilians_osv_rate, na.rm = TRUE),
         deaths_civilians_int_rate_avg = mean(deaths_civilians_int_rate, na.rm = TRUE),
         deaths_civilians_nsc_rate_avg = mean(deaths_civilians_nsc_rate, na.rm = TRUE))
df <- df[, c("country", "year", "period", "health_class", "gender_class", "class", "class_vv", "class1990", "class_vv1990", "class1995", "class_vv1995", "life_exp_wpp_avg", "imr_wpp_avg", "mys_age_ratio_ihme_avg", "asfr_adol_wpp_avg", "latentmean_fariss_avg", "v2caviol_avg", "v2clkill_avg", "v2cltort_avg", "hom_odcwho_rate_avg", "deaths_all_int_rate_avg", "deaths_all_nsc_rate_avg", "deaths_civilians_osv_rate_avg", "deaths_civilians_int_rate_avg", "deaths_civilians_nsc_rate_avg")]
df$period <- as.integer(str_sub(df$period, 7, 10))
df <- df[df$period == df$year & df$period %in% seq(1975, 2015, 5), names(df) != "year"]
# data.frame(class = table(df$period, is.na(df$class))[, 1],
#            life = table(df$period, is.na(df$life_exp_wpp_avg))[, 1],
#            imr = table(df$period, is.na(df$imr_wpp_avg))[, 1],
#            asfr = table(df$period, is.na(df$asfr_adol_wpp_avg))[, 1],
#            mys = table(df$period, is.na(df$mys_age_ratio_ihme_avg))[, 1])
class1975 <- df[IsTrue(df$period == 1975), c("country", "class", "health_class", "gender_class")]
class1975$class_vv <- NA
class1975$class_vv[class1975$health_class < 3 & class1975$gender_class < 3] <- "low"
class1975$class_vv[class1975$health_class > 3 & class1975$gender_class > 3] <- "upp"
class1975$class_vv[!(class1975$health_class < 3 & class1975$gender_class < 3) & !(class1975$health_class > 3 & class1975$gender_class > 3)] <- "mid"
class1975$class_vv[class1975$class_vv == "mid" & class1975$health_class > class1975$gender_class] <- "H>G"
class1975$class_vv[class1975$class_vv == "mid" & class1975$health_class < class1975$gender_class] <- "G>H"
names(class1975)[-1] <- paste(names(class1975)[-1], "1975", sep = "")
df <- merge(df, class1975, by = "country", all.x = TRUE)
df <- df[!is.na(df$country), ]
df <- df[!(df$country %in% missing_countries), ]
df$life_exp_wpp_avg <- as.numeric(scale(df$life_exp_wpp_avg))
df$imr_wpp_avg <- as.numeric(scale(df$imr_wpp_avg))
df$mys_age_ratio_ihme_avg <- as.numeric(scale(df$mys_age_ratio_ihme_avg))
df$asfr_adol_wpp_avg <- as.numeric(scale(df$asfr_adol_wpp_avg))
df$health <- rowMeans(df[, c("life_exp_wpp_avg", "imr_wpp_avg")], na.rm = FALSE)
df$gender <- rowMeans(df[, c("mys_age_ratio_ihme_avg", "asfr_adol_wpp_avg")], na.rm = FALSE)
df <- df %>% 
  arrange(country, period) %>% 
  group_by(country) %>% 
  mutate(lag_imr_wpp_avg = lag(imr_wpp_avg), 
         lag_asfr_adol_wpp_avg = lag(asfr_adol_wpp_avg),
         lag_life_exp_wpp_avg = lag(life_exp_wpp_avg),
         lag_mys_age_ratio_ihme_avg = lag(mys_age_ratio_ihme_avg),
         lag_health = lag(health),
         lag_gender = lag(gender))
mean_health <- mean(df$health, na.rm = TRUE)
range_health <- range(df$health, na.rm = TRUE)
mean_gender <- mean(df$gender, na.rm = TRUE)
range_gender <- range(df$gender, na.rm = TRUE)
range_both <- range(c(range_health, range_gender))
df$health_chg <- df$health - df$lag_health
df$gender_chg <- df$gender - df$lag_gender
df$distance <- sqrt((df$health_chg)^2 + (df$gender_chg)^2)
# df$slope <- (df$health - df$lag_health)/(df$gender - df$lag_gender)
df <- df %>% group_by(country) %>% mutate(total = sum(distance, na.rm = TRUE), first = min(period), last = max(period), periods = length(unique(period)))
first <- df[df$period == df$first, c("country", "first", "periods", "class_vv1975", "class_vv1995", "total", "health", "gender")]
names(first)[7:8] <- paste("first", names(first)[7:8], sep = "_")
last <- df[df$period == df$last, c("country", "health", "gender")]
names(last)[-1] <- paste("last", names(last)[-1], sep = "_")
new <- merge(first, last, by = "country")
new$distance <- sqrt((new$last_health - new$first_health)^2 + (new$last_gender - new$first_gender)^2)
new$dist_total <- new$distance / new$total
new$dist_period <- new$distance / new$periods
new$health_period <- (new$last_health - new$first_health) / new$periods
new$gender_period <- (new$last_gender - new$first_gender) / new$periods
new[, -c(1:5)] <- lapply(new[, -c(1:5)], round, 3)
vars <- c("dist_total", "dist_period", "health_period", "gender_period")
new[, paste(vars, "quart", sep = "_")] <- lapply(new[, vars], function(col) {
  new <- rep(NA, length(col))
  new[col >= quantile(col, na.rm = TRUE)[1]] <- "1st quartile"
  new[col >= quantile(col, na.rm = TRUE)[2]] <- "2nd quartile"
  new[col >= quantile(col, na.rm = TRUE)[3]] <- "3rd quartile"
  new[col >= quantile(col, na.rm = TRUE)[4]] <- "4th quartile"
  return(as.factor(new))
})
new <- new[, !names(new) %in% c("last_health", "first_health", "last_gender", "first_gender")]
new <- merge(seq[, names(seq)[!str_detect(names(seq), "sequence")]], new, by = "country", all = TRUE)
new <- merge(new, violence, by = "country", all = TRUE)
df <- merge(df, seq[, names(seq)[!str_detect(names(seq), "sequence")]], by = "country", all = TRUE)
df <- merge(df, violence, by = "country", all = TRUE)
```

```{r cross-tabs, include = FALSE, fig.show = "hide"}
new$class_vv1975 <- factor(new$class_vv1975, levels = c("low", "G>H", "H>G", "mid", "upp"))
new$class_vv1995 <- factor(new$class_vv1995, levels = c("low", "G>H", "H>G", "mid", "upp"))
table(new$class_vv1975, useNA = "ifany")
table(new$class_vv1995, useNA = "ifany")
new$conflict_1976_1995 <- factor(new$conflict_1976_1995, levels = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"))
new$conflict_1976_2015 <- factor(new$conflict_1976_2015, levels = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"))
new$conflict_1996_2015 <- factor(new$conflict_1996_2015, levels = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"))
# round(addmargins(prop.table(table(new[, c("conflict_1976_2015", "class_vv1975")]), margin = 2), margin = 1), 3) * 100
ggplot(data = new[!is.na(new$class_vv1975), ], 
       mapping = aes(x = class_vv1975, fill = conflict_1976_2015)) +
  geom_bar(stat = "count", position = position_dodge2(preserve = "single")) +
  scale_fill_discrete(limits = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"), name = "") +
  theme_minimal() + 
  theme(legend.position = "top", legend.key.size = unit(0.3, 'cm')) + 
  labs(y = "Number of countries", x = "")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/class_conflict_1975_1976.pdf")
# round(addmargins(prop.table(table(new[, c("conflict_1976_2015", "class_vv1995")]), margin = 2), margin = 1), 3) * 100
ggplot(data = new[!is.na(new$class_vv1975), ], 
       mapping = aes(x = class_vv1975, fill = conflict_1996_2015)) +
  geom_bar(stat = "count", position = position_dodge2(preserve = "single")) +
  scale_fill_discrete(limits = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"), name = "") +
  theme_minimal() + 
  theme(legend.position = "top", legend.key.size = unit(0.3, 'cm')) + 
  labs(y = "Number of countries", x = "")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/class_conflict_1975_1996.pdf")
# round(addmargins(prop.table(table(new[, c("conflict_1996_2015", "class_vv1995")]), margin = 2), margin = 1), 3) * 100
ggplot(data = new[!is.na(new$class_vv1995), ], 
       mapping = aes(x = class_vv1995, fill = conflict_1996_2015)) +
  geom_bar(stat = "count", position = position_dodge2(preserve = "single")) +
  scale_fill_discrete(limits = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"), name = "") +
  theme_minimal() + 
  theme(legend.position = "top", legend.key.size = unit(0.3, 'cm')) + 
  labs(y = "Number of countries", x = "")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/class_conflict_1995_1996.pdf")
# round(addmargins(prop.table(table(new[new$conflict_1976_1995 == "none", c("conflict_1996_2015", "class_vv1995")]), margin = 2), margin = 1), 3) * 100
ggplot(data = new[!is.na(new$class_vv1995) & new$conflict_1976_1995 == "none", ], 
       mapping = aes(x = class_vv1995, fill = conflict_1996_2015)) +
  geom_bar(stat = "count", position = position_dodge2(preserve = "single")) +
  scale_fill_discrete(limits = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"), name = "") +
  theme_minimal() + 
  theme(legend.position = "top", legend.key.size = unit(0.3, 'cm')) + 
  labs(y = "Number of countries", x = "")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/class_conflict_1995_1996_prenone.pdf")
# round(addmargins(prop.table(table(new[new$conflict_1976_1995 != "none", c("conflict_1996_2015", "class_vv1995")]), margin = 2), margin = 1), 3) * 100
ggplot(data = new[!is.na(new$class_vv1995) & new$conflict_1976_1995 != "none", ], 
       mapping = aes(x = class_vv1995, fill = conflict_1996_2015)) +
  geom_bar(stat = "count", position = position_dodge2(preserve = "single")) +
  scale_fill_discrete(limits = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"), name = "") +
  theme_minimal() + 
  theme(legend.position = "top", legend.key.size = unit(0.3, 'cm')) + 
  labs(y = "Number of countries", x = "")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/class_conflict_1995_1996_presome.pdf")
```

#### Countries
```{r countries, results = 'hide', out.width = "33%", out.height = "33%"}
lapply(unique(df$country), function(ctry) {
  ggplot(data = df[df$country == ctry  & df$period > 1975, ], # & !is.na(df$lag_health) & !is.na(df$lag_gender)
         mapping = aes(x = lag_gender, y = lag_health, xend = gender, yend = health) ) + 
    coord_fixed(ratio = 1) + 
    geom_vline(xintercept = mean_gender, color = "gray") + 
    geom_hline(yintercept = mean_health, color = "gray") + 
    geom_abline(intercept = 0, slope = 1, color = "gray") + 
    geom_segment(lineend = "round", mapping = aes(color = as.factor(period))) + 
    scale_color_manual(values = c("1975" = "gray", "1980" = "red", "1985" = "orange", "1990" = "red", "1995" = "orange", 
                                  "2000" = "purple", "2005" = "blue", "2010" = "purple", "2015" = "blue")) +
    geom_point(aes(x = lag_gender[period == min(period)], y = lag_health[period == min(period)]), 
               shape = 20, size = 0.75, color = "green", fill = "green") + 
    geom_point(aes(x = gender[period == max(period)], y = health[period == max(period)]), 
               shape = 20, size = 0.75, color = "red", fill = "red") + 
    coord_cartesian(xlim = range_both, ylim = range_both) + 
    labs(x = "Gender", y = "Health") + 
    theme_classic() + theme(legend.position = "none") + 
    ggtitle(label = ctry, subtitle = paste("\nfrom 1975: ", seq$typology1975[seq$country == ctry],
                                           "\nfrom 1995: ", seq$typology1995[seq$country == ctry]))
})
```

#### Classification {.tabset .tabset-fade .tabset-pills}

##### 1975
```{r class_1975, results = 'hide', out.width = "33%", out.height = "33%"}
lookup <- table(df$class_vv1975[df$period == 2015])
lookup["no 1975 classification"] <- sum(is.na(df$class_vv1975[df$period == 2015]))
plotClass <- function(class, dat, range) {
  ggplot(data = dat, 
         mapping = aes(x = lag_gender, y = lag_health, xend = gender, yend = health, group = country, color = country)) + 
    coord_fixed(ratio = 1) + 
    geom_vline(xintercept = mean_gender, color = "gray") + 
    geom_hline(yintercept = mean_health, color = "gray") + 
    geom_segment(lineend = "round", arrow = arrow(angle = 10, type = "open", length = unit(4, "points"))) + 
    labs(x = "Gender", y = "Health") + 
    coord_cartesian(xlim = range, ylim = range) + 
    theme_classic() + theme(legend.position = "none") + 
    ggtitle(paste(class, " (", lookup[class], ")", sep = ""))
}
lapply(c("low", "H>G", "G>H", "mid", "upp"), function(class) {
  to_show <- plotClass(class = class, 
            dat = df[df$class_vv1975 == class & df$period > 1975, ],
            range = range_both)
  ggsave(device = "pdf", plot = to_show, filename = paste("_figures/sequences_class1975_", class, ".pdf", sep = ""), width = 5, height = 5)
  to_show
})
plotClass(class = "no 1975 classification", 
          dat = df[is.na(df$class_vv1975) & df$period > 1975, ],
          range = range_both)
ggsave(device = "pdf", filename = "_figures/sequences_class1975_NA.pdf", width = 5, height = 5)
```

##### 1975 (from origin)
```{r class_1975_origin, results = 'hide', out.width = "33%", out.height = "33%"}
new1975 <- df[df$period > 1975 & !is.na(df$lag_gender) & !is.na(df$lag_health), ] %>% 
  arrange(country, period) %>% 
  group_by(country) %>% 
  mutate(first = min(period),
         health_first = lag_health[period == first],
         gender_first = lag_gender[period == first]) %>% 
  mutate(health = health - health_first,
         lag_health = lag_health - health_first,
         gender = gender - gender_first,
         lag_gender = lag_gender - gender_first)
# new1975 %>% select(country, period, first, health, lag_health, health_first, gender, lag_gender, gender_first) %>% print(n = 20) 
range_both_new <- range(c(range(new1975$gender, na.rm = TRUE), range(new1975$health, na.rm = TRUE)))
lapply(c("low", "H>G", "G>H", "mid", "upp"), function(class) {
  to_show <- plotClass(class = class, 
            dat = new1975[new1975$class_vv1975 == class, ], 
            range = range_both_new)
  ggsave(device = "pdf", plot = to_show, filename = paste("_figures/sequences_class1975_origin_", class, ".pdf", sep = ""), width = 5, height = 5)
  to_show
})
plotClass(class = "no 1975 classification", 
          dat = new1975[is.na(new1975$class_vv1975), ],
          range = range_both)
ggsave(device = "pdf", filename = "_figures/sequences_class1975_origin_NA.pdf", width = 5, height = 5)
```

##### 1995 
```{r class_1995, results = 'hide', out.width = "33%", out.height = "33%"}
lookup <- table(df$class_vv1995[df$period == 2015])
lookup["no 1995 classification"] <- sum(is.na(df$class_vv1995[df$period == 2015]))
lapply(c("low", "H>G", "G>H", "mid", "upp"), function(class) {
  to_show <- plotClass(class = class, 
            dat = df[df$class_vv1995 == class & df$period > 1995, ],
            range = range_both)
  ggsave(device = "pdf", plot = to_show, filename = paste("_figures/sequences_class1995_", class, ".pdf", sep = ""), width = 5, height = 5)
  to_show
})
plotClass(class = "no 1995 classification", 
          dat = df[is.na(df$class_vv1995) & df$period > 1995, ],
          range = range_both)
ggsave(device = "pdf", filename = "_figures/sequences_class1995_NA.pdf", width = 5, height = 5)
```

##### 1995 (from origin)
```{r class_1995_origin, results = 'hide', out.width = "33%", out.height = "33%"}
new1995 <- df[df$period > 1995 & !is.na(df$lag_gender) & !is.na(df$lag_health), ] %>%
  arrange(country, period) %>% 
  group_by(country) %>% 
  mutate(first = min(period))
# new1995$first[new1995$first < 1995] <- 1995
new1995 <- new1995 %>% 
  mutate(health_first = lag_health[period == first],
         gender_first = lag_gender[period == first]) %>% 
  mutate(health = health - health_first, 
         lag_health = lag_health - health_first,
         gender = gender - gender_first,
         lag_gender = lag_gender - gender_first)
# new1995 %>% select(country, period, first, health, lag_health, health_first, gender, lag_gender, gender_first) %>% print(n = 100) 
range_gender_new <- range(new1995$gender, na.rm = TRUE)
range_health_new <- range(new1995$health, na.rm = TRUE)
range_both_new <- range(c(range_gender_new, range_health_new))
lapply(c("low", "H>G", "G>H", "mid", "upp"), function(class) {
  to_show <- plotClass(class = class, 
            dat = new1995[new1995$class_vv1995 == class, ], 
            range = range_both_new)
  ggsave(device = "pdf", plot = to_show, filename = paste("_figures/sequences_class1995_origin_", class, ".pdf", sep = ""), width = 5, height = 5)
  to_show
})
plotClass(class = "no 1995 classification", 
          dat = new1995[is.na(new1995$class_vv1995), ],
          range = range_both)
ggsave(device = "pdf", filename = "_figures/sequences_class1995_origin_NA.pdf", width = 5, height = 5)

```

#### Typology {.tabset .tabset-fade .tabset-pills}

##### from 1975
```{r typology_1975, results = 'hide', out.width = "33%", out.height = "33%"}
plotCategory <- function(cat, dat, range) {
  ggplot(data = dat, 
         mapping = aes(x = lag_gender, y = lag_health, xend = gender, yend = health, group = country, color = country)) + 
    coord_fixed(ratio = 1) + 
    geom_segment(lineend = "round", arrow = arrow(angle = 10, type = "open", length = unit(5, "points"))) + 
    geom_vline(xintercept = mean_gender, color = "gray") + 
    geom_hline(yintercept = mean_health, color = "gray") + 
    labs(x = "Gender", y = "Health") + 
    coord_cartesian(xlim = range, ylim = range) + 
    theme_classic() + theme(legend.position = "none") + 
    ggtitle(paste(cat, " (", lookup[cat], ")", sep = ""))
}
lookup <- table(seq$typology1975)
lapply(sort(unique(df$typology1975)), function(sequ) {
  to_show <- plotCategory(cat = sequ,
    dat = df[df$typology1975 == sequ & df$period > 1975, ],
    range = range_both)
  ggsave(plot = to_show, filename = paste("_figures/sequences_typology1975_", which(names(lookup) == sequ), ".pdf", sep = ""), width = 5, height = 5)
  to_show
})
```

##### from 1995
```{r typology_1995, results = 'hide', out.width = "33%", out.height = "33%"}
lookup <- table(seq$typology1995)
lapply(sort(unique(df$typology1995)), function(sequ) {
  to_show <- plotCategory(cat = sequ, 
           dat = df[df$typology1995 == sequ & df$period > 1995, ], 
           range = range_both)
  ggsave(plot = to_show, filename = paste("_figures/sequences_typology1995_", which(names(lookup) == sequ), ".pdf", sep = ""), width = 5, height = 5)
  to_show
})
```

##### Data
```{r typology_table}
new[, c("country", "typology1975", "typology1995", "class_vv1975", "class_vv1995")]
```

#### Health & gender 

```{r summary}
new[, c("country", "first", "periods", "total", "distance", "dist_total", "dist_period", "health_period", "gender_period")]
summary(new[, c("first", "total", "distance", "dist_total", "dist_period", "health_period", "gender_period")])
```

#### Internal conflict
```{r sequences_conflict, results = 'hide', out.width = "33%", out.height = "33%"}
lookup <- table(new$conflict_1971_2015)
lapply(c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"), function(cat) {
  plotCategory(cat = cat, 
           dat = df[df$conflict_1971_2015 == cat & df$period > 1975, ], 
           range = range_both)
})
```

#### Bivariate distributions {.tabset .tabset-fade .tabset-pills}

##### Health change
```{r bivariate_health}
# round(addmargins(prop.table(table(new[, c("typology1975", "health_period_quart")]), margin = 1) * 100, margin = 2), 1)
data_summary <- function(x) {
  m <- mean(x)
  ymin <- quantile(x)[["25%"]]
  ymax <- quantile(x)[["75%"]]
  return(c(y = m, ymin = ymin, ymax = ymax))
}
ggplot(data = new, mapping = aes(x = health_period, y = typology1975)) +
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 18) +
  # stat_summary(fun.data = data_summary, geom = "pointrange") + 
  geom_vline(xintercept = 0, color = "gray") + 
  # coord_cartesian(xlim = c(0, NA)) + 
  labs(x = "Health change per period", y = "Sequence (1975-2015)") + 
  theme_minimal()
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_health.pdf")
```

##### Gender change
```{r bivariate_gender}
ggplot(data = new, mapping = aes(x = gender_period, y = typology1975)) +
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 18) +
  # stat_summary(fun.data = data_summary, geom = "pointrange") + 
  geom_vline(xintercept = 0, color = "gray") + 
  labs(x = "Gender change per period", y = "Sequence (1975-2015)") + 
  theme_minimal()
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_gender.pdf")
```

##### Overall change
```{r bivariate_both}
ggplot(data = new, mapping = aes(x = dist_period, y = typology1975)) +
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 18) +
  # stat_summary(fun.data = data_summary, geom = "pointrange") + 
  labs(x = "Health & gender change per period", y = "Sequence (1975-2015)") + 
  geom_vline(xintercept = 0, color = "gray") + 
  theme_minimal()
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_health_gender.pdf")
```

##### Path efficiency
```{r bivariate_efficiency}
ggplot(data = new, mapping = aes(x = dist_total, y = typology1975)) +
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 18) +
  # stat_summary(fun.data = data_summary, geom = "pointrange") + 
  geom_vline(xintercept = 0, color = "gray") + 
  labs(x = "Path efficiency", y = "Sequence (1975-2015)") + 
  theme_minimal()
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_efficiency.pdf")
```

##### Internal conflict
```{r conflict}
new$conflict_1971_2015 <- factor(new$conflict_1971_2015, levels = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"))
# round(addmargins(prop.table(table(new[, c("typology1975", "conflict_1971_2015")]), margin = 1), margin = 2), 3) * 100
ggplot(data = new, 
       mapping = aes(y = typology1975, fill = conflict_1971_2015)) +
  geom_bar(stat = "count", position = position_dodge2(preserve = "single")) +
  scale_fill_discrete(limits = c("none", "conflict", "conflict (5+ yrs)", "war", "war (5+ yrs)"), name = "") +
  theme_minimal() + 
  theme(legend.position = "top",
        legend.key.size = unit(0.3, 'cm')) + 
  labs(x = "Number of countries", y = "Sequence (1975-2015)")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_conflict.pdf")
```

##### LPI
```{r lpi}
# round(addmargins(prop.table(table(new[, c("typology1975", "latentmean_fariss_1971_2015")]), margin = 1) * 100, margin = 2), 1)
# addmargins(table(new[, c("typology1975", "latentmean_fariss_1971_2015")]))
ggplot(data = new, mapping = aes(x = latentmean_fariss_1971_2015, y = typology1975)) +
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 18) +
  # stat_summary(fun.data = data_summary, geom = "pointrange") + 
  theme_minimal() + 
  labs(x = "Average LPI", y = "Sequence (1975-2015)")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_lpi.pdf")
```

##### Extra-judicial killings
```{r killings}
ggplot(data = new, mapping = aes(x = v2clkill_1971_2015, y = typology1975)) +
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 18) +
  # stat_summary(fun.data = data_summary, geom = "pointrange") + 
  theme_minimal() + 
  labs(x = "Average extrajudicial killings score", y = "Sequence (1975-2015)")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_killings.pdf")
```

##### Societal violence
```{r societal}
ggplot(data = new, mapping = aes(x = v2caviol_1971_2015, y = typology1975)) +
  geom_boxplot() + 
  stat_summary(fun = mean, geom = "point", shape = 18) +
  # stat_summary(fun.data = data_summary, geom = "pointrange", color = "red") +
  theme_minimal() + 
  labs(x = "Average societal violence score", y = "Sequence (1975-2015)")
ggsave(device = "pdf", height = 4, width = 6.5, filename = "_figures/sequences_societal.pdf")
```

```{r violence_rates, fig.width = 10, fig.height = 10, echo = FALSE, eval = FALSE}
temp <- df %>% 
  arrange(country, period) %>% 
  group_by(period) %>% 
  select(country, period, typology1975, deaths_all_int_rate_avg, deaths_all_nsc_rate_avg, hom_odcwho_rate_avg) %>% 
  pivot_longer(-c(country, period, typology1975), names_to = "variable", values_to = "value")
ggplot(data = temp) + 
  stat_summary(mapping = aes(x = period, y = value, color = variable), fun = "mean", geom = "line") + 
  facet_wrap(~typology1975) + theme_classic() + theme(legend.position = "bottom")
```
